---
title: "Result_writeup"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=10, fig.height=5) 

```



```{r,include=FALSE}
source("function/linear.R")
source("function/formula.R")
source("function/R2Compute.R")
source("function/R2ComputeDF.R")

library("dplyr")
library("ggplot2")
``` 

```{r,include=FALSE}
clust_2010 <- read.csv("data/clust_2010.csv")
clust_2013 = read.csv("data/clust_2013.csv")

coord13 <- clust_2013 %>% 
  select(clust,fnid)


coord10 <- clust_2010 %>% 
  select(clust,fnid)

coord <- bind_rows(coord10,coord13)
colnames(coord) <- c("ea_id","fnid")

```


1.	summary stats (pooled data of 2010 and 2013)
  a.	FS by month plot 

```{r,include= FALSE}
malawi_hh<- read.csv("data/Malawi_aggregate.csv")
malawi_sub = malawi_hh %>% 
dplyr::filter(FS_year < 2015)

malawi_join<- dplyr::left_join(malawi_sub, coord, by = "ea_id")

malawi_13= malawi_hh %>% 
dplyr::filter(FS_year == 2013)

malawi_13_fs = malawi_sub %>% 
  select(rCSI,FCS,HDDS)


malawi_13_fs_wide = malawi_13_fs %>% 
  dplyr::mutate( logFCS = log(FCS))

malawi_13_fs_wide =  malawi_13_fs_wide %>%  select(-FCS)

long_malawi13 = malawi_13_fs_wide %>% tidyr::gather()
long_malawi13["no"] =1
long_malawi13["level"] ="Household Actual"

long_FCS_hh = long_malawi13   %>%  filter(key=="logFCS")
long_RCSI_hh = long_malawi13   %>%  filter(key=="rCSI")
long_HDDS_hh = long_malawi13   %>%  filter(key=="HDDS")

long_FCS_hh = long_FCS_hh   %>%  select(-key)
long_RCSI_hh = long_RCSI_hh   %>%  select(-key)
long_HDDS_hh = long_HDDS_hh   %>%  select(-key)

colnames(long_FCS_hh)[1] <- "logFCS"
colnames(long_RCSI_hh)[1] <- "RCSI"
colnames(long_HDDS_hh)[1] <- "HDDS"

```

```{r,echo=FALSE}
data = malawi_sub %>% 
  select(rCSI,FCS,HDDS,FS_month)
data<-as.data.frame(data)
data$rCSI[data$rCSI>42]<-42
data<-data[data$HDDS!=0,]


short_data<-aggregate(cbind(rCSI,FCS,HDDS)~FS_month,data=data, mean)
library(reshape2)
long_data<- melt(short_data,na.rm=TRUE,id.vars = c("FS_month"),measure.vars = c("rCSI","FCS","HDDS"))

colnames(long_data)<-c("month","measure","Food_security")
long_data$months<-as.factor(long_data$month)


FCS_long<-as.data.frame(long_data[long_data$measure=="FCS",])

p<-ggplot(as.data.frame(long_data[long_data$measure!="FCS",]),aes(x=months,color=measure,y=Food_security,shape = measure,group=measure)) + theme_bw() + geom_path(size=2.5)+ geom_point(size=5)  
# adding the relative humidity data, transformed to match roughly the range of the temperature
p <- p +geom_line(size=2.5,data=FCS_long,aes(y = Food_security/12.3, colour = measure))  + geom_point(data=FCS_long,aes(y = Food_security/12.3, colour = measure),size=5)  


# now adding the secondary axis, following the example in the help file ?scale_y_continuous
# and, very important, reverting the above transformation
p <- p + scale_y_continuous(sec.axis = sec_axis(~.*12.3, name = "Food consumption scores"))

# modifying colours and theme options
#  p <- p + scale_colour_manual(values = c("blue", "red"))
p <- p + labs(y = "HDDS and RCSI scores",
              x = "Month",
              colour = "Food Security Measures",
              shape= " ")
p
```

  b.	bar chart of variation 
```{r,include=FALSE}
data = malawi_join %>% 
  select(rCSI,FCS,HDDS,FS_month,fnid,TA_names,ea_id)


data$month_clust <-interaction(data$FS_month,data$ea_id)
data$rCSI[data$rCSI>42]<-42
data<-data[data$HDDS!=0,]

colnames(data)[4] <-"Month"
colnames(data)[5] <-"IPC"
colnames(data)[6] <-"TA"
colnames(data)[7] <-"Cluster"
colnames(data)[8] <-"month_clust"

 
#	Maybe a bar chart of variation in FS security measures (month, IPCzone, TA, cluster, month x cluster)

r2 = matrix(NA,3,5)
my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(Month),data=data))
summaries <- lapply(my_lms, summary)
r2[,1]<-sapply(summaries, function(x) c(r_sq = x$r.squared))


my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(IPC),data=data))
summaries <- lapply(my_lms, summary)
r2[,2]<-sapply(summaries, function(x) c(r_sq = x$r.squared))


my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(TA),data=data))
summaries <- lapply(my_lms, summary)
r2[,3]<-sapply(summaries, function(x) c(r_sq = x$r.squared))


my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(Cluster),data=data))
summaries <- lapply(my_lms, summary)
r2[,4]<-sapply(summaries, function(x) c(r_sq = x$r.squared))



my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(month_clust),data=data))
summaries <- lapply(my_lms, summary)
r2[,5]<-sapply(summaries, function(x) c(r_sq = x$r.squared))


r2 <-as.data.frame(r2)

colnames(r2)<-c("Month","IPC","TA","Cluster","Cluster_by_month")
rownames(r2)<-c("RCSI","FCS","HDDS")
#r2$measure<-c("RCSI","FCS","HDDS")


long_r2<- melt(t(r2),na.rm=TRUE,measure.vars =c("RCSI","FCS","HDDS"))
long_r2<-long_r2[long_r2$Var1!="measure",]

colnames(long_r2)<-c("variation","measure","rsquares")

ar<-as.character(long_r2$rsquares)
long_r2$ar<-as.numeric(ar)


# RCSI_r2_fe =  .22320556
# HDDS_r2_fe =  .30987621
# logFCS_r2_fe =  .33045673
 
```
```{r,echo=FALSE}
p<-ggplot(long_r2, aes(variation,ar)) +geom_bar(stat = "identity",position = "dodge",aes(fill = measure))

p <- p + labs(y = "R squares",
              x = " ",
              colour = "Food Security Measures",
              shape= " ")

p <- p+ theme_bw() 
p <- p + theme(text = element_text(size=22)) 
p              
```



```{r,include=FALSE}

# levels 
levels<-c("ipczone","TA","clust")

# variables 
weather<-c("L12raincytot","L12day1rain","L12maxdays","floodmax")
access<-c("lag_price","lag_thinn")
asset1 <-c("roof","cells_own")
land<-c("percent_ag","elevation","nutri_reten_constrained")
distance<-c("dist_road","dist_admarc")
demo<-c("hhsize","hh_age","hh_gender","asset")

model3_variables<-c(weather,access,asset1,land,distance,demo)
model2_variables<-c(weather,access,asset1,land,distance)
model1_variables<-c(weather,access,land,distance)

# goal : combine variables at different levels using pastes 
# output: variables lists at different levels, TA_vars, ipczone vars, etc. 

for (level in levels){
  # assign levels of variables group
  group_var_name<-paste(level,"vars",sep="_")
  assign(group_var_name,c())
  
  for(var in model3_variables){
    temp<-paste(level,var,sep = "_")
    new<-append(get(group_var_name),temp)
    assign(group_var_name,new)
  }
}

### 1. Linear/tobit Results 

# Create the formulas using the formula_compose function. 

rcsi_formula<-formula_compose("clust_RCSI",clust_vars)
logFCS_formula<-formula_compose("clust_logFCS",clust_vars)
HDDS_formula<-formula_compose("clust_HDDS",clust_vars)

rcsi_predictions<-linear_fit(rcsi_formula,clust_2010,clust_2013)
logFCS_predictions<-linear_fit(logFCS_formula,clust_2010,clust_2013) 
HDDS_predictions<-linear_fit(HDDS_formula,clust_2010,clust_2013) 

rcsi_pair <- cbind(clust_2013$clust_RCSI, rcsi_predictions)
logFCS_pair <- cbind(clust_2013$clust_logFCS, logFCS_predictions)
HDDS_pair <- cbind(clust_2013$clust_HDDS, HDDS_predictions)

colnames(rcsi_pair) <- c("actual","predict")
colnames(logFCS_pair) <- c("actual","predict")
colnames(HDDS_pair) <- c("actual","predict")


linear_list<- list(rcsi_pair,logFCS_pair,HDDS_pair)


r2list<- sapply(linear_list,R2Compute)
 r2list= format(r2list, digits=3, nsmall=2)
```



2.	Result of 2013 prediction 

a.	Scatter plots (predict vs. actual) 
```{r,echo=FALSE}
ggplot(as.data.frame(rcsi_pair), aes(actual, predict )) +
  geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
  theme_minimal() + geom_abline(intercept = 0, slope = 1)+
  scale_color_brewer(palette="Dark2") +
  annotate(geom = "text", size = 5, x = 11, y = 1.5, label = paste("R Squares = ",r2list[1],sep = " ")) +
  labs(x = "Cluster Average RCSI (Actual)", y = "Cluster Average RCSI (Predicted)")


ggplot(as.data.frame(logFCS_pair), aes(actual, predict)) +
  geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
  theme_minimal() + geom_abline(intercept = 0, slope = 1)+
  scale_color_brewer(palette="Dark2") +
  annotate(geom = "text", size = 5, x = 4.28, y = 3.75, label = paste("R Squares = ",r2list[2],sep = " ")) +
  labs(x = "Cluster Average logFCS (Actual)", y = "Cluster Average logFCS (Predicted)")


ggplot(as.data.frame(HDDS_pair), aes(actual, predict)) +
  geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
  theme_minimal() + geom_abline(intercept = 0, slope = 1)+
  scale_color_brewer(palette="Dark2")+
  annotate(geom = "text", size = 5, x = 6.5, y = 4.5, label = paste("R Squares = ",r2list[3],sep = " "))+
  labs(x = "Cluster Average HDDS (Actual)", y = "Cluster Average HDDS (Predicted)")

```
b.	Density plot (predication using different scales + household)
    i.	Unexplored variation of household level 
```{r,echo=FALSE}    
csv_list <- list.files(path="data/all_predict", 
                    pattern = "csv$",
                    full.names=TRUE)
dfnames<-csv_list

# remove irregulars in the file names, 
pattern<-c("data/all_predict/","clust_",".csv")
for (i in 1:length(pattern)) {
  dfnames <- gsub(pattern[i],"", dfnames)
}



list2env(
  lapply(setNames(csv_list, make.names(dfnames)), 
         function(i){read.csv(i)}), envir = .GlobalEnv)

predict_df<-cbind(logFCS_predict_m3[1],RCSI_predict_m3[1],HDDS_predict_m3[1])

for (i in 1:length(dfnames)){
  # exclude unneeded cols  
  temp <- get(dfnames[i])
  predict_df<-cbind(predict_df,temp[2])
}




malawi<- read.csv("data/cluster_fs.csv")
 
logFCS_IPC <- read.csv("data/all_ipc/logFCS_predict_CLUST_IPC.csv")
HDDS_IPC <- read.csv("data/all_ipc/HDDS_predict_CLUST_IPC.csv")
RCSI_IPC <- read.csv("data/all_ipc/RCSI_predict_CLUST_IPC.csv")

 
    
FCS_data<-cbind(predict_df$clust_logFCS_ipczone_predict_m3,predict_df$clust_logFCS_TA_predict_m3,predict_df$clust_logFCS_clust_predict_m3,predict_df$clust_logFCS,logFCS_IPC$clust_logFCS_predict_ipc)
colnames(FCS_data)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")
long_fcs<- melt(FCS_data,na.rm=TRUE)
colnames(long_fcs)<-c("no","level","logFCS")
plot_long<- long_fcs[long_fcs$level != "IPC_value_only",]
plot_long_ipc_fcs<- long_fcs[long_fcs$level == "IPC_value_only",]


plot_long_FCS= dplyr::bind_rows(plot_long, long_FCS_hh)



HDDS_data<-cbind(predict_df$clust_HDDS_ipczone_predict_m3,predict_df$clust_HDDS_TA_predict_m3,predict_df$clust_HDDS_clust_predict_m3,predict_df$clust_HDDS,HDDS_IPC$clust_HDDS_predict_ipc)
colnames(HDDS_data)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")
long_HDDS<- melt(HDDS_data,na.rm=TRUE)
colnames(long_HDDS)<-c("no","level","HDDS")
plot_long<- long_HDDS[long_HDDS$level != "IPC_value_only",]
plot_long_ipc_HDDS<- long_HDDS[long_HDDS$level == "IPC_value_only",]

plot_long_HDDS= dplyr::bind_rows(plot_long, long_HDDS_hh)


# rcsi P1 < 4
#P2 = 4-17
#P3 = 17-42
#P4/5 > 42
RCSI_data<-cbind(predict_df$clust_RCSI_ipczone_predict_m3,predict_df$clust_RCSI_TA_predict_m3,predict_df$clust_RCSI_clust_predict_m3,predict_df$clust_RCSI,RCSI_IPC$clust_RCSI_predict_ipc)
colnames(RCSI_data)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")
long_rcsi<- melt(RCSI_data,na.rm=TRUE)
colnames(long_rcsi)<-c("no","level","RCSI")
plot_long<- long_rcsi[long_rcsi$level != "IPC_value_only",]
plot_long_ipc_RCSI<- long_rcsi[long_rcsi$level == "IPC_value_only",]

plot_long_RCSI= dplyr::bind_rows(plot_long, long_RCSI_hh)


``` 

```{r,echo= FALSE}
p = ggplot(as.data.frame(plot_long_FCS),aes(x=logFCS,color=level)) + geom_density(alpha=0.1) +xlim(2.8, 4.9) +
geom_vline(xintercept=log(28),linetype=2) + geom_vline(xintercept=log(42),linetype=2)+
  stat_density(data=plot_long_ipc_fcs,aes(x=logFCS, y=..scaled..*3.5,color=level)) + scale_y_continuous(sec.axis = sec_axis(~.*28, name = " density (IPC value only) ")) +  
 theme_bw()

 p
 
 
 
p= ggplot(as.data.frame(plot_long_HDDS),aes(x=HDDS, color=level))+ geom_density(alpha=0.25,show.legend = TRUE) +
  xlim(1.5, 7.6) + geom_vline(xintercept=3,linetype=2) + geom_vline(xintercept=6,linetype=2) +
  stat_density(data=plot_long_ipc_HDDS,aes(x=HDDS,y=..scaled..*1.1,color=level)) +
  scale_y_continuous(name= "density",sec.axis = sec_axis(~.*12, name = "density (IPC value only) "))  +  theme_bw()

p
 


p = ggplot(as.data.frame(plot_long_RCSI),aes(x=RCSI, color=level))+ stat_density(data=plot_long_ipc_RCSI,aes(x=RCSI,y=..scaled../2.3,color=level)) + geom_density(alpha=0.25)+xlim(0, 45) + 
  geom_vline(xintercept=4,linetype=2) + geom_vline(xintercept=17,linetype=2)+ geom_vline(xintercept=42,linetype=2)+
   scale_y_continuous(name= "density",sec.axis = sec_axis(~.*3.125, name = "density (IPC value only) ")) +
  theme_bw()
p
 
```
    
  
    
d.	 R squares of 2013 predication 

```{r,echo=FALSE}
FCS_data_model3 =  FCS_data 


FCS_data_model2<-cbind(predict_df$clust_logFCS_ipczone_predict_m2,predict_df$clust_logFCS_TA_predict_m2,predict_df$clust_logFCS_clust_predict_m2,predict_df$clust_logFCS,logFCS_IPC$clust_logFCS_predict_ipc)
colnames(FCS_data_model2)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")



FCS_data_model1<-cbind(predict_df$clust_logFCS_ipczone_predict_m1,predict_df$clust_logFCS_TA_predict_m1,predict_df$clust_logFCS_clust_predict_m1,predict_df$clust_logFCS,logFCS_IPC$clust_logFCS_predict_ipc)
colnames(FCS_data_model1)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")

FCS_List<-list(FCS_data_model1,FCS_data_model2,FCS_data_model3)

HDDS_data_model3 =  HDDS_data 


HDDS_data_model2<-cbind(predict_df$clust_HDDS_ipczone_predict_m2,predict_df$clust_HDDS_TA_predict_m2,predict_df$clust_HDDS_clust_predict_m2,predict_df$clust_HDDS,HDDS_IPC$clust_HDDS_predict_ipc)
colnames(HDDS_data_model2)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")



HDDS_data_model1<-cbind(predict_df$clust_HDDS_ipczone_predict_m1,predict_df$clust_HDDS_TA_predict_m1,predict_df$clust_HDDS_clust_predict_m1,predict_df$clust_HDDS,HDDS_IPC$clust_HDDS_predict_ipc)
colnames(HDDS_data_model1)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")

HDDS_List<-list(HDDS_data_model1,HDDS_data_model2,HDDS_data_model3)


RCSI_data_model3 =  RCSI_data 


RCSI_data_model2<-cbind(predict_df$clust_RCSI_ipczone_predict_m2,predict_df$clust_RCSI_TA_predict_m2,predict_df$clust_RCSI_clust_predict_m2,predict_df$clust_RCSI,RCSI_IPC$clust_RCSI_predict_ipc)
colnames(RCSI_data_model2)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")



RCSI_data_model1<-cbind(predict_df$clust_RCSI_ipczone_predict_m1,predict_df$clust_RCSI_TA_predict_m1,predict_df$clust_RCSI_clust_predict_m1,predict_df$clust_RCSI,RCSI_IPC$clust_RCSI_predict_ipc)
colnames(RCSI_data_model1)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")

RCSI_List<-list(RCSI_data_model1,RCSI_data_model2,RCSI_data_model3)
source("function/R2Compute.R")
source("function/R2ComputeDF.R")


r2mat_RCSI<- sapply(RCSI_List,R2ComputeDF)
r2mat_HDDS<- sapply(HDDS_List,R2ComputeDF)
r2mat_FCS<- sapply(FCS_List,R2ComputeDF)

colnames(r2mat_RCSI) = c("m1","m2","m3")
colnames(r2mat_HDDS) = c("m1","m2","m3")
colnames(r2mat_FCS) = c("m1","m2","m3")

rownames(r2mat_RCSI) = c("IPC_zone","TA","cluster","IPC_value_only")
rownames(r2mat_HDDS) = c("IPC_zone","TA","cluster","IPC_value_only")
rownames(r2mat_FCS) = c("IPC_zone","TA","cluster","IPC_value_only")


r2matlist<-list(r2mat_FCS,r2mat_HDDS,r2mat_RCSI)

r2matlist<-lapply(r2matlist,as.data.frame)
r2matlist<-lapply(r2matlist,function(x){tibble::rownames_to_column(x,var = "level")})

r2matlist<-lapply(r2matlist,function(x){tidyr::gather(data= x,key=level, value = rsquares)})

r2matlist[[1]]["measure"] ="FCS"
r2matlist[[2]]["measure"] ="HDDS"
r2matlist[[3]]["measure"] ="RCSI"

r2 = bind_rows(r2matlist[[1]],r2matlist[[2]],r2matlist[[3]])
colnames(r2)[2] = "Model"

r2$level[r2$level=="IPC_zone"]<-"IPC Zone"
r2$level[r2$level=="cluster"]<-"Cluster"
r2$model_num[r2$Model=="m1"]<-"Model 1"
r2$model_num[r2$Model=="m2"]<-"Model 2"
r2$model_num[r2$Model=="m3"]<-"Model 3"

ord <- c("IPC_value_only","IPC Zone","TA","Cluster")
r2$level <- factor(r2$level,levels=ord)

r2$rsquares <-as.numeric(r2$rsquares)

rplot<-ggplot(data = r2, aes(x =level, y = rsquares,colour = Model ,shape = measure)) 
rplot<-rplot + geom_point(size=7)
rplot<-rplot + labs( x = "Geo-spatial level", y = "R Squared")

rplot <- rplot+ theme_bw() 
rplot <- rplot + theme(text = element_text(size=22)) 
print(rplot + scale_colour_manual(values = c("Blue", "Red", "Green")))


``` 
    
    
    
f.	 Discussion of classification 
g.  hit and miss tables (for the predications) 
    i.	one is cluster to actual cluster outcomes 
    
    
```{r,echo=FALSE}
library(caret)
logFCS <- read.csv("data/all_predict/clust_logFCS_predict_clust_m3.csv")
HDDS <- read.csv("data/all_predict/clust_HDDS_predict_clust_m3.csv")
RCSI <- read.csv("data/all_predict/clust_RCSI_predict_clust_m3.csv")

colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")

#"Poor_predict","Borderline_predict","Acceptable_predict"
# Poor_actual","Borderline_actual","Acceptable_actual"

logFCS$cat_logFCS<-cut(logFCS$logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS$cat_logFCS_predict<-cut(logFCS$logFCS_predict, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
print("logFCS confusionMatrix")

confusionMatrix(logFCS$cat_logFCS_predict,logFCS$cat_logFCS)

# HDDS 3 6 
HDDS$cat_HDDS<-cut(HDDS$HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS$cat_HDDS_predict<-cut(HDDS$HDDS_predict, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
print("HDDS confusionMatrix")
confusionMatrix(HDDS$cat_HDDS_predict,HDDS$cat_HDDS)



RCSI$cat_RCSI<-cut(RCSI$RCSI, c(-Inf,4,17,42,Inf),labels=c("Severe","Moderate","Mild","Food Secure"))
RCSI$cat_RCSI_predict<-cut(RCSI$RCSI_predict, c(-Inf,4,17,42,Inf),labels=c("Severe","Moderate","Mild","Food Secure"))

print("RCSI confusionMatrix")

confusionMatrix(RCSI$cat_RCSI_predict,RCSI$cat_RCSI)


```
    
    
    
    
    
    
```{r,include=FALSE}
hh_2010 <- read.csv("data/IHS2010.csv")
hh_2013 = read.csv("data/IHS2013.csv")


rcsi_formula_hh<-formula_compose("RCSI",clust_vars)
logFCS_formula_hh<-formula_compose("logFCS",clust_vars)
HDDS_formula_hh<-formula_compose("HDDS",clust_vars)

rcsi_coord <- cbind(clust_2013$clust, rcsi_predictions)
logFCS_coord <- cbind(clust_2013$clust, logFCS_predictions)
HDDS_coord <- cbind(clust_2013$clust, HDDS_predictions)

colnames(rcsi_coord) = c("clust","rcsi_predict")
colnames(logFCS_coord) = c("clust","logFCS_predict")
colnames(HDDS_coord) = c("clust","HDDS_predict")


rcsi_predictions_hh<-linear_fit(rcsi_formula_hh,hh_2010,hh_2013)
logFCS_predictions_hh<-linear_fit(logFCS_formula_hh,hh_2010,hh_2013) 
HDDS_predictions_hh<-linear_fit(HDDS_formula_hh,hh_2010,hh_2013) 

```
    
    
   ii.	cluster predication to actual household level outcomes 
```{r,echo=FALSE}

hh_actual  = hh_2010 %>% select(clust,logFCS,HDDS,RCSI) %>% na.omit()


hh_join = dplyr::left_join(hh_actual,as.data.frame(rcsi_coord) , by = "clust")
hh_join = dplyr::left_join(hh_join,as.data.frame(logFCS_coord) , by = "clust")
hh_join = dplyr::left_join(hh_join,as.data.frame(HDDS_coord) , by = "clust")


logFCS = hh_join %>% select(logFCS,logFCS_predict)
RCSI = hh_join %>% select(RCSI,rcsi_predict)
HDDS = hh_join %>% select(HDDS,HDDS_predict)


colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")

#"Poor_predict","Borderline_predict","Acceptable_predict"
# Poor_actual","Borderline_actual","Acceptable_actual"

logFCS$cat_logFCS<-cut(logFCS$logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS$cat_logFCS_predict<-cut(logFCS$logFCS_predict, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))

print("logFCS confusionMatrix")

confusionMatrix(logFCS$cat_logFCS_predict,logFCS$cat_logFCS)


# HDDS 3 6 
HDDS$cat_HDDS<-cut(HDDS$HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS$cat_HDDS_predict<-cut(HDDS$HDDS_predict, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))

print("HDDS confusionMatrix")
confusionMatrix(HDDS$cat_HDDS_predict,HDDS$cat_HDDS)



RCSI$cat_RCSI<-cut(RCSI$RCSI, c(-Inf,4,17,42,Inf),labels=c("Severe","Moderate","Mild","Food Secure"))
RCSI$cat_RCSI_predict<-cut(RCSI$RCSI_predict, c(-Inf,4,17,42,Inf),labels=c("Severe","Moderate","Mild","Food Secure"))

print("RCSI confusionMatrix")
confusionMatrix(RCSI$cat_RCSI_predict,RCSI$cat_RCSI)

```


    1.	how bad it can be to just target the cluster level ?
    
    
    2.	put it in SI ? 
    
    
    
3.	2010 data (only what matters for 2010 is the tables (coefficients and variables))

a.	regression results 




b.	discussion on the coefficients 






```{r,include=FALSE}
# train= clust_2010 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              clust_logFCS,clust_RCSI,clust_HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# test= clust_2013 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              clust_logFCS,clust_RCSI,clust_HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# write.csv(train,"train.csv")
# write.csv(test,"test.csv")

```

```{r,include=FALSE}
# library(dplyr)
# trainHH= IHS2010 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              logFCS,RCSI,HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# testHH= IHS2013 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              logFCS,RCSI,HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# write.csv(trainHH,"trainhh.csv")
# write.csv(testHH,"testhh.csv")

```

```{r,include= FALSE}
cat("the overlapping months in 2010 and 2013 are" ,as.character(unique(clust_2013$month)))

common_lhz= intersect(unique(clust_2010$fnid),unique(clust_2013$fnid))

cat("and the number of overlapping ipc zones is" ,length(common_lhz))
```


```{r,include=FALSE}

string=c()
for (i in 1:length(common_lhz)){
  st1 <- paste("gen lhz",i,sep="")
  st2 <- paste(st1,"= 1 if fnid==")
  st3<-paste(st2,as.character(common_lhz)[i])
  string<-append(string,st3)
}
string
write.table(string, "~/Desktop/statadum.txt", sep="")
fileConn <- file("test.out")    
writeLines(string, fileConn)    
close(fileConn)
```

```{r,include= FALSE}
# library("ggpubr")
# ggscatter(logFCS_pair, x = "actual", y = "predict",
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = FALSE, cor.method = "pearson",
#           xlab = "actual", ylab = "predict")
# 
# ggsave("logFCS_scatter.png", plot = last_plot(),device = "png",path = "output/figures/",
#        dpi = 1000, limitsize = TRUE)
# 
# ggscatter(d, x ="RCSI_cluster" , y = "RCSI_pred",
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = TRUE, cor.method = "pearson",
#           xlab = "actual", ylab = "predict")
# 
# ggsave("RCSI_scatter.png", plot = last_plot(),device = "png",path = "output/figures/",
#        dpi = 1000, limitsize = TRUE)
# 
# ggscatter(d, x ="HDDS_cluster" , y = "HDDS_pred",
#           add = "reg.line", conf.int = TRUE, 
#           cor.coef = FALSE, cor.method = "pearson",
#           xlab = "actual", ylab = "predict")
# 
# ggsave("HDDS_scatter.png", plot = last_plot(),device = "png",path = "output/figures/",
#        dpi = 1000, limitsize = TRUE)


```