---
title: "Result_writeup"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=15, fig.height=10) 

```



```{r,include=FALSE}
source("function/linear.R")
source("function/formula.R")
source("function/R2Compute.R")
source("function/R2ComputeDF.R")

library("dplyr")
library("ggplot2")
require(grid)
library(reshape2)

``` 

```{r,include=FALSE}
clust_2010 <- read.csv("data/clust_2010.csv")
clust_2013 = read.csv("data/clust_2013.csv")

coord13 <- clust_2013 %>% 
  select(clust,fnid)


coord10 <- clust_2010 %>% 
  select(clust,fnid)

coord <- bind_rows(coord10,coord13)
colnames(coord) <- c("ea_id","fnid")

```


1.	summary stats (pooled data of 2010 and 2013)
  a.	FS by month plot 

```{r,include= FALSE}
malawi_hh<- read.csv("data/Malawi_aggregate.csv")
malawi_sub = malawi_hh %>% 
dplyr::mutate( logFCS = log(FCS)) %>% 
dplyr::filter(FS_year < 2015)

malawi_join<- dplyr::left_join(malawi_sub, coord, by = "ea_id")

malawi_13= malawi_hh %>% 
dplyr::filter(FS_year == 2013)

malawi_10= malawi_hh %>% 
dplyr::filter(FS_year < 2013)

malawi_13_fs = malawi_sub %>% 
  select(rCSI,logFCS,HDDS)

long_malawi13 = malawi_13_fs %>% tidyr::gather()
long_malawi13["no"] =1
long_malawi13["level"] ="Household Actual"

long_FCS_hh = long_malawi13   %>%  filter(key=="logFCS")
long_RCSI_hh = long_malawi13   %>%  filter(key=="rCSI")
long_HDDS_hh = long_malawi13   %>%  filter(key=="HDDS")

long_FCS_hh = long_FCS_hh   %>%  select(-key)
long_RCSI_hh = long_RCSI_hh   %>%  select(-key)
long_HDDS_hh = long_HDDS_hh   %>%  select(-key)

colnames(long_FCS_hh)[1] <- "logFCS"
colnames(long_RCSI_hh)[1] <- "RCSI"
colnames(long_HDDS_hh)[1] <- "HDDS"

```

```{r,echo=FALSE}
data = malawi_sub %>% 
  select(rCSI,logFCS,HDDS,FS_month)
data<-as.data.frame(data)
data$rCSI[data$rCSI>42]<-42
data<-data[data$HDDS!=0,]

data %>% group_by(FS_month) %>% dplyr::summarise(avg=mean(rCSI,na.rm = TRUE))

short_data<-aggregate(cbind(rCSI,logFCS,HDDS)~FS_month,data=data, mean)
library(reshape2)
long_data<- melt(short_data,na.rm=TRUE,id.vars = c("FS_month"),measure.vars = c("rCSI","logFCS","HDDS"))

colnames(long_data)<-c("month","measure","Food_security")
long_data$months<-as.factor(long_data$month)




ord_measure <- c("rCSI","logFCS","HDDS")
long_data$measure <- factor(long_data$measure,levels=ord_measure)


FCS_long<-as.data.frame(long_data[long_data$measure=="logFCS",])

p<-ggplot(as.data.frame(long_data[long_data$measure!="logFCS",]),aes(x=months,color=measure,y=Food_security,group=measure)) + theme_classic() + geom_path(size=2.5,show.legend = FALSE)+ geom_point(size=5,show.legend = FALSE)  
# adding the relative humidity data, transformed to match roughly the range of the temperature
p <- p +geom_line(size=2.5,data=FCS_long,aes(y = Food_security*1.1, colour = measure,))  + geom_point(data=FCS_long,aes(y = Food_security*1.1,colour = measure),show.legend = FALSE,size=5)  
p = p +   theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=17), legend.text=element_text(size=16),axis.text.x=element_text(size=17),axis.text.y=element_text(size=17),
                 axis.title=element_text(size=17,face="bold") ) 
 
# now adding the secondary axis, following the example in the help file ?scale_y_continuous
# and, very important, reverting the above transformation
p <- p + scale_y_continuous(sec.axis = sec_axis(~./1.1, name = "Food consumption scores (in log forms) "))
# p = p + scale_color_grey()
# modifying colours and theme options
p <- p + scale_colour_manual(values = c("#619CFF", "#00BA38","#F8766D"))+ theme(legend.position = "bottom")
p <- p + labs(y = "HDDS and rCSI scores",
              x = "Month",
              colour = "Food Security Measures",
              shape= " ")
p
```

  b.	bar chart of variation 
```{r,include=FALSE}
data = malawi_join %>% select(rCSI,logFCS,HDDS,FS_month,fnid,TA_names,ea_id)


data$month_clust <-interaction(data$FS_month,data$ea_id)
data$rCSI[data$rCSI>42]<-42 
data<-data[data$HDDS!=0,]

colnames(data)[4] <-"Month" 
colnames(data)[5] <-"IPC" 
colnames(data)[6] <-"TA"
colnames(data)[7] <-"Cluster" 
colnames(data)[8] <-"Month+Cluster"


#	Maybe a bar chart of variation in FS security measures (month, IPCzone, TA, cluster, month x cluster)

r2 = matrix(NA,3,5) 
my_lms <- lapply(1:3, function(x) lm(data[,x] ~as.factor(Month),data=data)) 
summaries <- lapply(my_lms, summary)
r2[,1]<-sapply(summaries, function(x) c(r_sq = x$r.squared))


my_lms <- lapply(1:3, function(x) 
lm(data[,x] ~ as.factor(IPC),data=data))
summaries <- lapply(my_lms, summary) 
r2[,2]<-sapply(summaries, function(x)
  c(r_sq = x$r.squared))


my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(TA),data=data))
summaries <- lapply(my_lms, summary) 
r2[,3]<-sapply(summaries, function(x)
c(r_sq = x$r.squared))


my_lms <- lapply(1:3, function(x) lm(data[,x] ~ as.factor(Cluster),data=data))
summaries <- lapply(my_lms, summary) 
r2[,4]<-sapply(summaries, function(x)
c(r_sq = x$r.squared))



my_lms <- lapply(1:3, function(x) lm(data[,x] ~as.factor(Month+Cluster),data=data)) 
summaries <- lapply(my_lms, summary)
r2[,5]<-sapply(summaries, function(x) c(r_sq = x$r.squared))


r2 <-as.data.frame(r2)

colnames(r2)<-c("Month","IPC","TA","Cluster","Cluster + Month")
rownames(r2)<-c("rCSI","logFCS","HDDS") #r2$measure<-c("RCSI","FCS","HDDS")


long_r2<- melt(t(r2),na.rm=TRUE,measure.vars =c("rCSI","logFCS","HDDS"))
long_r2<-long_r2[long_r2$Var1!="measure",]

colnames(long_r2)<-c("variation","Measures","Rsquared")

ar<-as.character(long_r2$Rsquared)
long_r2$ar<-as.numeric(ar)


# RCSI_r2_fe =  .22320556
# HDDS_r2_fe =  .30987621
# logFCS_r2_fe =  .33045673
 
```

```{r,echo=FALSE}
p<-ggplot(long_r2, aes(variation,ar)) +geom_bar(stat = "identity",position = "dodge",aes(fill = Measures))

p <- p + labs(y = "R Squared",
              x = " ",
              colour = "Food Security Measures",
              shape= " ")

p <- p+ theme_classic()
p <- p +theme(plot.title = element_text(size = 30, face = "bold"),legend.title=element_text(size=30), legend.text=element_text(size=30),axis.text.x=element_text(size=30),axis.text.y=element_text(size=30),
                 axis.title=element_text(size=30,face="bold") )
p = p + scale_fill_grey(start = 0.2,end = 0.8)
p
```



```{r,include=FALSE}

# levels 
levels<-c("ipczone","TA","clust")

# variables 
weather<-c("L12raincytot","L12day1rain","L12maxdays","floodmax")
access<-c("lag_price","lag_thinn")
asset1 <-c("roof","cells_own")
land<-c("percent_ag","elevation","nutri_reten_constrained")
distance<-c("dist_road","dist_admarc")
demo<-c("hhsize","hh_age","hh_gender","asset")

model3_variables<-c(weather,access,asset1,land,distance,demo)
model2_variables<-c(weather,access,asset1,land,distance)
model1_variables<-c(weather,access,land,distance)

# goal : combine variables at different levels using pastes 
# output: variables lists at different levels, TA_vars, ipczone vars, etc. 

for (level in levels){
  # assign levels of variables group
  group_var_name<-paste(level,"vars",sep="_")
  assign(group_var_name,c())
  
  for(var in model3_variables){
    temp<-paste(level,var,sep = "_")
    new<-append(get(group_var_name),temp)
    assign(group_var_name,new)
  }
}

### 1. Linear/tobit Results 

# Create the formulas using the formula_compose function. 

rcsi_formula<-formula_compose("clust_RCSI",clust_vars)
logFCS_formula<-formula_compose("clust_logFCS",clust_vars)
HDDS_formula<-formula_compose("clust_HDDS",clust_vars)

rcsi_predictions<-linear_fit(rcsi_formula,clust_2010,clust_2013)
logFCS_predictions<-linear_fit(logFCS_formula,clust_2010,clust_2013) 
HDDS_predictions<-linear_fit(HDDS_formula,clust_2010,clust_2013) 

rcsi_pair <- cbind(clust_2013$clust_RCSI, rcsi_predictions)
logFCS_pair <- cbind(clust_2013$clust_logFCS, logFCS_predictions)
HDDS_pair <- cbind(clust_2013$clust_HDDS, HDDS_predictions)

colnames(rcsi_pair) <- c("actual","predict")
colnames(logFCS_pair) <- c("actual","predict")
colnames(HDDS_pair) <- c("actual","predict")


linear_list<- list(rcsi_pair,logFCS_pair,HDDS_pair)


r2list<- sapply(linear_list,R2Compute)
 r2list= format(r2list, digits=3, nsmall=2)
```



2.	Result of 2013 prediction 

a.	Scatter plots (predict vs. actual) 
```{r,echo=FALSE}
cutoff1 <- data.frame( x = c(-Inf, Inf), y = 17, cutoff = factor(17) )
cutoff2 <- data.frame( x = c(-Inf, Inf), y = 4, cutoff = factor(4) )
cutoff3 <- data.frame( y = c(-Inf, Inf), x = 17, cutoff = factor(17) )
cutoff4 <- data.frame( y = c(-Inf, Inf), x = 4, cutoff = factor(4) )

# 28 42 3 6 
rcsi_pair = as.data.frame(rcsi_pair)
rcsi_pair$predict[rcsi_pair$predict<0 & is.na(rcsi_pair$predict)==FALSE] =0

ggplot(rcsi_pair, aes(actual, predict )) +
  
  theme_classic() + geom_abline(intercept = 0, slope = 1)+
  scale_color_brewer(palette="Dark2") +
theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
                 axis.title=element_text(size=17,face="bold") )  +
  labs(x = "Cluster Average RCSI (Actual)", y = "Cluster Average rCSI (Predicted)") +
  theme(plot.margin = unit(c(1, 10, 1, 1), "lines"))  +

  geom_line(aes( x, y, linetype = cutoff), cutoff1,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoff2,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoff3,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoff4,show.legend = FALSE) +
  geom_ribbon(data=subset(as.data.frame(rcsi_pair), 0 <= actual & actual <= 4), 
          aes(ymin=0,ymax=actual), fill="grey", alpha="0.45")+   # area 2 left 
    geom_ribbon(data=subset(as.data.frame(rcsi_pair), 4 <= actual & actual <= 17), 
          aes(ymin=4,ymax=actual), fill="grey", alpha="0.45")+   # area 2 right 
  geom_ribbon(data=subset(as.data.frame(rcsi_pair), 4 <= actual & actual <= 17), 
          aes(ymin=actual,ymax=17), fill="grey", alpha="0.2")+   # area 3 right
  geom_ribbon(data=subset(as.data.frame(rcsi_pair), 0 <= actual & actual <= 4), 
          aes(ymin=actual,ymax=4), fill="grey", alpha="0.2") +  # area 3 left
  geom_ribbon(data=subset(as.data.frame(rcsi_pair), 0 <= actual & actual <= 4), 
          aes(ymin=4,ymax=17), fill="grey", alpha="0.6") +        # area 4 
  geom_ribbon(data=subset(as.data.frame(rcsi_pair), 4 <= actual & actual <= 17), 
          aes(ymin=0,ymax=4), fill="grey", alpha="0.8") +           # area 1
  geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
 annotate(geom = "text", size = 7, x = 10, y = 7, label = "IIb") +
 annotate(geom = "text", size = 7, x = 2.2, y = 0.5, label = "IIa") +
  annotate(geom = "text", size = 7, x = 10, y = 2, label = "I") +
   annotate(geom = "text", size = 7, x = 0.2, y = 3, label = "IIIa") +
  annotate(geom = "text", size = 7, x = 7, y = 10, label = "IIIb") +
  annotate(geom = "text", size = 7, x = 2, y = 10, label = "IV") 

 grid.text(paste("R Squared= ",r2list[1],sep = " "), x = unit(0.85, "npc"), y = unit(0.65, "npc"),gp=gpar(fontsize=14),just="left") 

 grid.text("Cutoff: 0 <= rCSI < 4", x = unit(0.85, "npc"), y = unit(0.57, "npc"),gp=gpar(fontsize=14),just="left") 
  grid.text("is food secure; ", x = unit(0.85, "npc"), y = unit(0.54, "npc"),gp=gpar(fontsize=14),just="left") 
 grid.text("4 <= rCSI < 17 is ", x = unit(0.85, "npc"), y = unit(0.51, "npc"),gp=gpar(fontsize=14),just="left") 
  grid.text("midly food insecure;", x = unit(0.85, "npc"), y = unit(0.48, "npc"),gp=gpar(fontsize=14),just="left") 
 grid.text("rCSI >= 17 is ", x = unit(0.85, "npc"), y = unit(0.45, "npc"),gp=gpar(fontsize=14),just="left") 
  grid.text("moderately or severely", x = unit(0.85, "npc"), y = unit(0.42, "npc"),gp=gpar(fontsize=14),just="left") 
 grid.text("food insecure.", x = unit(0.85, "npc"), y = unit(0.39, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# 
#  grid.text("Area I: Overpredicting; mildly food ", x = unit(0.85, "npc"), y = unit(0.41, "npc"),gp=gpar(fontsize=14),just="left") 
#   grid.text("insecure predicted as food secure", x = unit(0.85, "npc"), y = unit(0.38,"npc"),gp=gpar(fontsize=14),just="left") 
#  grid.text("Area IIa: Overpredicting within food secure", x = unit(0.85, "npc"), y = unit(0.35, "npc"),gp=gpar(fontsize=14),just="left") 
#   grid.text("Area IIb: Overpredicting within mildly", x = unit(0.85, "npc"), y = unit(0.32, "npc"),gp=gpar(fontsize=14),just="left") 
#   grid.text("food insecure", x = unit(0.85, "npc"), y = unit(0.29, "npc"),gp=gpar(fontsize=14),just="left") 
# 
# grid.text("Area IIIa: Underpredicting within food secure", x = unit(0.85, "npc"), y = unit(0.26, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area IIIb: Underpredicting within mildly", x = unit(0.85, "npc"), y = unit(0.23, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("food insecure", x = unit(0.85, "npc"), y = unit(0.20, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IV: Underpredicting; secure", x = unit(0.85, "npc"), y = unit(0.17, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("predicted as mildly insecure", x = unit(0.85, "npc"), y = unit(0.14, "npc"),gp=gpar(fontsize=15),just="left") 



cutoffa <- data.frame( x = c(-Inf, Inf), y =3.332, cutoff = factor(3.332) )
cutoffb <- data.frame( x = c(-Inf, Inf), y = 3.738, cutoff = factor(3.738)  )
cutoffc <- data.frame( y = c(-Inf, Inf), x =3.332, cutoff = factor(3.332)  )
cutoffd <- data.frame( y = c(-Inf, Inf), x = 3.738, cutoff = factor(3.738)  )

ggplot(as.data.frame(logFCS_pair), aes(actual, predict)) +
  
  theme_classic() + geom_abline(intercept = 0, slope = 1)+
theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
                 axis.title=element_text(size=17,face="bold") ) +
  scale_color_brewer(palette="Dark2") +
  labs(x = "Cluster Average logFCS (Actual)", y = "Cluster Average logFCS (Predicted)") + 
  geom_line(aes( x, y, linetype = cutoff), cutoffa,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoffb,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoffc,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoffd,show.legend = FALSE) +
  geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.332 <= actual & actual <= 3.738), 
              aes(ymin=3.332,ymax=actual), fill="grey", alpha="0.2") +   # area 3 left 
  geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.738 <= actual & actual <= 4.6), 
              aes(ymin=3.738,ymax=actual), fill="grey", alpha="0.2") +   # area 3 right 
  geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.332 <= actual & actual <= 3.738), 
              aes(ymin=actual,ymax=3.738), fill="grey", alpha="0.45") +   # area 2 left
  geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.738 <= actual & actual <= 4.6), 
              aes(ymin=actual,ymax=4.7), fill="grey", alpha="0.45") +            # area 2 right
  geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.332<= actual & actual <= 3.738), 
              aes(ymin=3.738,ymax=4.7), fill="grey", alpha="0.8") +        # area 1
  geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.738 <= actual & actual <= 4.6), 
              aes(ymin=3.332,ymax=3.738), fill="grey", alpha="0.6") +           # area 4
  geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
  annotate(geom = "text", size = 7, x = 3.6, y = 3.5, label = "IIIa") +
  annotate(geom = "text", size = 7, x = 4.2, y = 3.9, label = "IIIb") +
  annotate(geom = "text", size = 7, x = 3.55, y = 4.15, label = "I") +
  annotate(geom = "text", size = 7, x = 3.55, y = 3.65, label = "IIa") +
  annotate(geom = "text", size = 7, x = 3.9, y = 4.2, label = "IIb") +
  annotate(geom = "text", size = 7, x = 4, y = 3.5, label = "IV") +
  theme(plot.margin = unit(c(1, 11, 1, 1), "lines")) 

grid.text(paste("R Squared= ",r2list[2],sep = " "), x = unit(0.84, "npc"), y = unit(0.65, "npc"),gp=gpar(fontsize=15),just="left") 

grid.text("Cutoff: 0 <= logFCS ", x = unit(0.84, "npc"), y = unit(0.57, "npc"),gp=gpar(fontsize=15),just="left") 
grid.text("< 3.33 is poor;", x = unit(0.84, "npc"), y = unit(0.54, "npc"),gp=gpar(fontsize=15),just="left") 

grid.text("3.33 <= logFCS ", x = unit(0.84, "npc"), y = unit(0.51, "npc"),gp=gpar(fontsize=15),just="left") 
grid.text("< 3.74 is borderline;", x = unit(0.84, "npc"), y = unit(0.48, "npc"),gp=gpar(fontsize=15),just="left") 

grid.text("logFCS >= 3.74 ", x = unit(0.84, "npc"), y = unit(0.45, "npc"),gp=gpar(fontsize=15),just="left") 
grid.text("is acceptable.", x = unit(0.84, "npc"), y = unit(0.42, "npc"),gp=gpar(fontsize=15),just="left") 

# grid.text("Area I: Overpredicting; borderline  ", x = unit(0.85, "npc"), y = unit(0.35, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("predicted as acceptable", x = unit(0.85, "npc"), y = unit(0.32,"npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area IIa: Overpredicting within acceptable", x = unit(0.85, "npc"), y = unit(0.29, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area IIb: Overpredicting within borderline", x = unit(0.85, "npc"), y = unit(0.26, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IIIa: Underpredicting within acceptable", x = unit(0.85, "npc"), y = unit(0.23, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area IIIb: Underpredicting within borderline", x = unit(0.85, "npc"), y = unit(0.20, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IV: Underpredicting; acceptable", x = unit(0.85, "npc"), y = unit(0.17, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("predicted as borderline", x = unit(0.85, "npc"), y = unit(0.14, "npc"),gp=gpar(fontsize=15),just="left") 

  


cutoffw <- data.frame( x = c(-Inf, Inf), y = 3, cutoff = factor(3) )
cutoffx <- data.frame( x = c(-Inf, Inf), y = 6, cutoff = factor(6) )
cutoffy <- data.frame( y = c(-Inf, Inf), x = 3, cutoff = factor(3) )
cutoffz <- data.frame( y = c(-Inf, Inf), x = 6, cutoff = factor(6) )

ggplot(as.data.frame(HDDS_pair), aes(actual, predict)) +
  theme_classic() + geom_abline(intercept = 0, slope = 1)+
  theme(plot.margin = unit(c(1, 10, 1, 1), "lines"))  +
  theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
                 axis.title=element_text(size=17,face="bold") ) +
  scale_color_brewer(palette="Dark2")+
  labs(x = "Cluster Average HDDS (Actual)", y = "Cluster Average HDDS (Predicted)") +
  geom_line(aes( x, y, linetype = cutoff), cutoffw,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoffx,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoffy,show.legend = FALSE) +
  geom_line(aes( x, y, linetype = cutoff), cutoffz,show.legend = FALSE)+
    geom_rect(data=as.data.frame(HDDS_pair), mapping=aes(xmin=3.01, xmax=4.1, ymin=6.01, ymax=8), fill="grey", alpha=0.03) +
    geom_rect(data=as.data.frame(HDDS_pair), mapping=aes(xmin=3.01, xmax=4.1, ymin=6.01, ymax=8), fill="grey", alpha=0.03) +

  geom_ribbon(data=subset(as.data.frame(HDDS_pair), 3 <= actual & actual <= 6), 
              aes(ymin=3,ymax=actual), fill = "grey" , alpha="0.2") +   # area 3 left 
  geom_ribbon(data=subset(as.data.frame(HDDS_pair), 6 <= actual & actual <= 7), 
              aes(ymin=6,ymax=actual), fill="grey", alpha="0.2") +   # area 3 right 
  geom_ribbon(data=subset(as.data.frame(HDDS_pair), 3 <= actual & actual <= 6), 
              aes(ymin=actual,ymax=6), fill="grey", alpha="0.45") +   # area 2 left
  geom_ribbon(data=subset(as.data.frame(HDDS_pair), 6 <= actual & actual <= 7), 
              aes(ymin=actual,ymax=8), fill="grey", alpha="0.45") +            # area 2 right
  geom_ribbon(data=subset(as.data.frame(HDDS_pair), 0<= actual & actual <= 6), 
              aes(ymin=6,ymax=8), fill="grey", alpha="0.8") +        # area 1
  geom_ribbon(data=subset(as.data.frame(HDDS_pair), 6 <= actual & actual <= 7), 
              aes(ymin=3,ymax=6), fill="grey", alpha="0.6") +           # area 4
    geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +

  annotate(geom = "text", size = 7, x = 4.7, y = 3.8, label = "IIIa") +
  annotate(geom = "text", size = 7, x = 6.5, y = 6.2, label = "IIIb") +
  annotate(geom = "text", size = 7, x = 4.7, y = 6.5, label = "I") +
  annotate(geom = "text", size = 7, x = 4.7, y = 5.6, label = "IIa") +
  annotate(geom = "text", size = 7, x = 6.5, y = 6.7, label = "IIb") +
  annotate(geom = "text", size = 7, x = 6.5, y = 3.8, label = "IV") 

grid.text(paste("R Squared= ",r2list[3],sep = " "), x = unit(0.85, "npc"), y = unit(0.65, "npc"),gp=gpar(fontsize=15),just="left") 

grid.text("Cutoff: 0 <= HDDS < 3 ", x = unit(0.85, "npc"), y = unit(0.58, "npc"),gp=gpar(fontsize=15),just="left") 
grid.text("is poor diversity;", x = unit(0.85, "npc"), y = unit(0.55, "npc"),gp=gpar(fontsize=15),just="left") 
grid.text("3 <= HDDS < 6 ", x = unit(0.85, "npc"), y = unit(0.52, "npc"),gp=gpar(fontsize=15),just="left")
grid.text("is medium diversity;", x = unit(0.85, "npc"), y = unit(0.49, "npc"),gp=gpar(fontsize=15),just="left")
grid.text("HDDS >= 6", x = unit(0.85, "npc"), y = unit(0.46, "npc"),gp=gpar(fontsize=15),just="left") 
grid.text("is good diversity.", x = unit(0.85, "npc"), y = unit(0.43, "npc"),gp=gpar(fontsize=15),just="left") 

# grid.text("Area I: Overpredicting; medium diversity", x = unit(0.85, "npc"), y = unit(0.46, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("predicted as good diversity", x = unit(0.85, "npc"), y = unit(0.43,"npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area IIa: Overpredicting within medium ", x = unit(0.85, "npc"), y = unit(0.40, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("diversity", x = unit(0.85, "npc"), y = unit(0.37, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IIb: Overpredicting within good diversity", x = unit(0.85, "npc"), y = unit(0.34, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IIIa: Underpredicting within medium", x = unit(0.85, "npc"), y = unit(0.31, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("diversity", x = unit(0.85, "npc"), y = unit(0.28, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IIIb: Underpredicting within good diversity", x = unit(0.85, "npc"), y = unit(0.30, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IV: Underpredicting; good diversity", x = unit(0.85, "npc"), y = unit(0.22, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("predicted as medium diversity", x = unit(0.85, "npc"), y = unit(0.19, "npc"),gp=gpar(fontsize=15),just="left") 








```

b.	Scatter plots (predict vs. actual) plus ipc only value 
```{r,include=FALSE}
# logFCS_IPC <- read.csv("data/all_ipc/logFCS_predict_CLUST_IPC.csv")
# HDDS_IPC <- read.csv("data/all_ipc/HDDS_predict_CLUST_IPC.csv")
# RCSI_IPC <- read.csv("data/all_ipc/RCSI_predict_CLUST_IPC.csv")
# 
# rcsi_pair <- cbind(as.matrix(rcsi_pair), RCSI_IPC$clust_RCSI_predict_ipc)
# colnames(rcsi_pair)[3] = "ipc_pred"
# 
# cutoff1 <- data.frame( x = c(-Inf, Inf), y = 17, cutoff = factor(17) )
# cutoff2 <- data.frame( x = c(-Inf, Inf), y = 4, cutoff = factor(4) )
# cutoff3 <- data.frame( y = c(-Inf, Inf), x = 17, cutoff = factor(17) )
# cutoff4 <- data.frame( y = c(-Inf, Inf), x = 4, cutoff = factor(4) )
# 
# # 28 42 3 6 
# 
# ggplot(as.data.frame(rcsi_pair), aes(actual, predict )) +
#   theme_classic() + geom_abline(intercept = 0, slope = 1)+
#   scale_color_brewer(palette="Dark2") +
#   labs(x = "Cluster Average RCSI (Actual)", y = "Cluster Average rCSI (Predicted)")+
# theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
#                  axis.title=element_text(size=17,face="bold") ) +
#   geom_line(aes( x, y, linetype = cutoff), cutoff1) +
#   geom_line(aes( x, y, linetype = cutoff), cutoff2) +
#   geom_line(aes( x, y, linetype = cutoff), cutoff3) +
#   geom_line(aes( x, y, linetype = cutoff), cutoff4) +
#   theme(plot.margin = unit(c(1, 14, 1, 1), "lines"))  +
#    geom_ribbon(data=subset(as.data.frame(rcsi_pair), 0 <= actual & actual <= 4), 
#           aes(ymin=0,ymax=actual), fill="grey", alpha="0.45")+   # area 2 left 
#     geom_ribbon(data=subset(as.data.frame(rcsi_pair), 4 <= actual & actual <= 17), 
#           aes(ymin=4,ymax=actual), fill="grey", alpha="0.45")+   # area 2 right 
#   geom_ribbon(data=subset(as.data.frame(rcsi_pair), 4 <= actual & actual <= 17), 
#           aes(ymin=actual,ymax=17), fill="grey", alpha="0.2")+   # area 3 right
#   geom_ribbon(data=subset(as.data.frame(rcsi_pair), 0 <= actual & actual <= 4), 
#           aes(ymin=actual,ymax=4), fill="grey", alpha="0.2") +  # area 3 left
#   geom_ribbon(data=subset(as.data.frame(rcsi_pair), 0 <= actual & actual <= 4), 
#           aes(ymin=4,ymax=17), fill="grey", alpha="0.6") +        # area 4 
#   geom_ribbon(data=subset(as.data.frame(rcsi_pair), 4 <= actual & actual <= 17), 
#           aes(ymin=0,ymax=4), fill="grey", alpha="0.8") +           # area 1
#     geom_point(data = as.data.frame(RCSI_IPC),aes(clust_RCSI, clust_RCSI_predict_ipc),shape =2,size =4,show.legend = FALSE,na.rm = TRUE) +
#     geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
# 
#  annotate(geom = "text", size = 7, x = 10, y = 7, label = "II") +
#  annotate(geom = "text", size = 7, x = 2.2, y = 0.5, label = "II") +
#   annotate(geom = "text", size = 7, x = 10, y = 2, label = "I") +
#    annotate(geom = "text", size = 7, x = 0.2, y = 3, label = "III") +
#   annotate(geom = "text", size = 7, x = 7, y = 10, label = "III") +
#   annotate(geom = "text", size = 7, x = 2, y = 10, label = "IV") +
#    theme(plot.margin = unit(c(1, 14, 1, 1), "lines"))  
# 
#  grid.text(paste("R Squared= ",r2list[1],sep = " "), x = unit(0.85, "npc"), y = unit(0.65, "npc"),gp=gpar(fontsize=15),just="left") 
#  grid.text("IPC only predictions in triangles", x = unit(0.85, "npc"), y = unit(0.62, "npc"),gp=gpar(fontsize=15)，just="left") 
#  grid.text("Cluster model predictions in dots", x = unit(0.85, "npc"), y = unit(0.59, "npc"),gp=gpar(fontsize=15)，just="left")
# 
#  grid.text("rCSI from 0 to 4 is food secure ", x = unit(0.85, "npc"), y = unit(0.44, "npc"),gp=gpar(fontsize=15),just="left") 
#  grid.text("rCSI from 4 to 17 is mildly insecure", x = unit(0.85, "npc"), y = unit(0.41, "npc"),gp=gpar(fontsize=15),just="left") 
#  grid.text("rCSI of 17 or above is moderately ", x = unit(0.85, "npc"), y = unit(0.38, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("or severely insecure ", x = unit(0.85, "npc"), y = unit(0.35, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# 
#  grid.text("Area I:Overpredicting, actually mildly", x = unit(0.85, "npc"), y = unit(0.31, "npc"),gp=gpar(fontsize=15),just="left") 
#   grid.text("insecure and predicted as secure", x = unit(0.85, "npc"), y = unit(0.28,"npc"),gp=gpar(fontsize=15),just="left") 
#  grid.text("Area II:Overpredicting,", x = unit(0.85, "npc"), y = unit(0.30, "npc"),gp=gpar(fontsize=15),just="left") 
#   grid.text("but within the same category", x = unit(0.85, "npc"), y = unit(0.22, "npc"),gp=gpar(fontsize=15),just="left") 
# 
#  
# grid.text("Area III:Underpredicting,", x = unit(0.85, "npc"), y = unit(0.19, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("but within the same category", x = unit(0.85, "npc"), y = unit(0.16, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IV:Underpredicting,actually secure", x = unit(0.85, "npc"), y = unit(0.13, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("and predicted as mildly insecure", x = unit(0.85, "npc"), y = unit(0.10, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# 
# 
# 
# 
# 
# 
# cutoffa <- data.frame( x = c(-Inf, Inf), y =3.332, cutoff = factor(3.332) )
# cutoffb <- data.frame( x = c(-Inf, Inf), y = 3.738, cutoff = factor(3.738) )
# cutoffc <- data.frame( y = c(-Inf, Inf), x =3.332, cutoff = factor(3.332) )
# cutoffd <- data.frame( y = c(-Inf, Inf), x = 3.738, cutoff = factor(3.738) )
# 
# ggplot(as.data.frame(logFCS_pair), aes(actual, predict)) +
#   theme_classic() + geom_abline(intercept = 0, slope = 1)+
#   scale_color_brewer(palette="Dark2") +
#   labs(x = "Cluster Average logFCS (Actual)", y = "Cluster Average logFCS (Predicted)") + 
#   geom_line(aes( x, y, linetype = cutoff), cutoffa) +
#   geom_line(aes( x, y, linetype = cutoff), cutoffb) +
#   geom_line(aes( x, y, linetype = cutoff), cutoffc) +
#   geom_line(aes( x, y, linetype = cutoff), cutoffd) +
#   theme(plot.margin = unit(c(1, 14, 1, 1), "lines"))  +
# theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
#                  axis.title=element_text(size=17,face="bold") ) +
#   geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.332 <= actual & actual <= 3.738), 
#               aes(ymin=3.332,ymax=actual), fill="grey", alpha="0.2") +   # area 3 left 
#   geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.738 <= actual & actual <= 4.6), 
#               aes(ymin=3.738,ymax=actual), fill="grey", alpha="0.2") +   # area 3 right 
#   geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.332 <= actual & actual <= 3.738), 
#               aes(ymin=actual,ymax=3.738), fill="grey", alpha="0.45") +   # area 2 left
#   geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.738 <= actual & actual <= 4.6), 
#               aes(ymin=actual,ymax=4.7), fill="grey", alpha="0.45") +            # area 2 right
#   geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.332<= actual & actual <= 3.738), 
#               aes(ymin=3.738,ymax=4.7), fill="grey", alpha="0.8") +        # area 1
#   geom_ribbon(data=subset(as.data.frame(logFCS_pair), 3.738 <= actual & actual <= 4.6), 
#               aes(ymin=3.332,ymax=3.738), fill="grey", alpha="0.6") +           # area 4
#     geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
#   geom_point(data = as.data.frame(logFCS_IPC),aes(clust_logFCS, clust_logFCS_predict_ipc),shape =2,size =4,show.legend = FALSE,na.rm = TRUE) +
# 
#   annotate(geom = "text", size = 7, x = 3.6, y = 3.5, label = "III") +
#   annotate(geom = "text", size = 7, x = 4.2, y = 3.9, label = "III") +
#   annotate(geom = "text", size = 7, x = 3.55, y = 4.15, label = "I") +
#   annotate(geom = "text", size = 7, x = 3.55, y = 3.65, label = "II") +
#   annotate(geom = "text", size = 7, x = 3.9, y = 4.2, label = "II") +
#   annotate(geom = "text", size = 7, x = 4, y = 3.5, label = "IV") +
#   theme(plot.margin = unit(c(1, 15, 1, 1), "lines")) 
# 
# grid.text(paste("R Squared= ",r2list[2],sep = " "), x = unit(0.85, "npc"), y = unit(0.65, "npc"),gp=gpar(fontsize=15),just="left") 
#   grid.text("IPC only predictions in triangles", x = unit(0.85, "npc"), y = unit(0.62, "npc"),gp=gpar(fontsize=15)，just="left") 
#   grid.text("Cluster model predictions in dots", x = unit(0.85, "npc"), y = unit(0.59, "npc"),gp=gpar(fontsize=15)，just="left")
# 
# grid.text("logFCS of 3.738 or above is acceptable", x = unit(0.85, "npc"), y = unit(0.47, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("logFCS from 3.332 to 3.738 is borderline", x = unit(0.85, "npc"), y = unit(0.44, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("logFCS of value 3.332 or below is poor", x = unit(0.85, "npc"), y = unit(0.41, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area I:Overpredicting, actually borderline", x = unit(0.85, "npc"), y = unit(0.38, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("status and predicted as acceptable", x = unit(0.85, "npc"), y = unit(0.35,"npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area II:Overpredicting,", x = unit(0.85, "npc"), y = unit(0.32, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("but within the same category", x = unit(0.85, "npc"), y = unit(0.29, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area III:Underpredicting,", x = unit(0.85, "npc"), y = unit(0.26, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("but within the same category", x = unit(0.85, "npc"), y = unit(0.23, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IV:Underpredicting,actually ", x = unit(0.85, "npc"), y = unit(0.2, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("acceptable and predicted as borderline", x = unit(0.85, "npc"), y = unit(0.17, "npc"),gp=gpar(fontsize=15),just="left") 
# 
#   
# 
# 
# cutoffw <- data.frame( x = c(-Inf, Inf), y = 3, cutoff = factor(3) )
# cutoffx <- data.frame( x = c(-Inf, Inf), y = 6, cutoff = factor(6) )
# cutoffy <- data.frame( y = c(-Inf, Inf), x = 3, cutoff = factor(3) )
# cutoffz <- data.frame( y = c(-Inf, Inf), x = 6, cutoff = factor(6) )
# 
# ggplot(as.data.frame(HDDS_pair), aes(actual, predict)) +
#   theme_classic() + geom_abline(intercept = 0, slope = 1)+
#   scale_color_brewer(palette="Dark2")+
# theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
#                  axis.title=element_text(size=17,face="bold") ) +
#   labs(x = "Cluster Average HDDS (Actual)", y = "Cluster Average HDDS (Predicted)") +
#   geom_line(aes( x, y, linetype = cutoff), cutoffw) +
#   geom_line(aes( x, y, linetype = cutoff), cutoffx) +
#   geom_line(aes( x, y, linetype = cutoff), cutoffy) +
#   geom_line(aes( x, y, linetype = cutoff), cutoffz) +
#   theme(plot.margin = unit(c(1, 14, 1, 1), "lines")) +
#   geom_ribbon(data=subset(as.data.frame(HDDS_pair), 3 <= actual & actual <= 6), 
#               aes(ymin=3,ymax=actual), fill="grey", alpha="0.2") +   # area 3 left 
#   geom_ribbon(data=subset(as.data.frame(HDDS_pair), 6 <= actual & actual <= 7), 
#               aes(ymin=6,ymax=actual), fill="grey", alpha="0.2") +   # area 3 right 
#   geom_ribbon(data=subset(as.data.frame(HDDS_pair), 3 <= actual & actual <= 6), 
#               aes(ymin=actual,ymax=6), fill="grey", alpha="0.45") +   # area 2 left
#   geom_ribbon(data=subset(as.data.frame(HDDS_pair), 6 <= actual & actual <= 7), 
#               aes(ymin=actual,ymax=8), fill="grey", alpha="0.45") +            # area 2 right
#   geom_ribbon(data=subset(as.data.frame(HDDS_pair), 3<= actual & actual <= 6), 
#               aes(ymin=6,ymax=8), fill="grey", alpha="0.8") +        # area 1
#   geom_ribbon(data=subset(as.data.frame(HDDS_pair), 6 <= actual & actual <= 7), 
#               aes(ymin=3,ymax=6), fill="grey", alpha="0.6") +           # area 4
#     geom_point(shape = 16, size = 3, show.legend = FALSE,na.rm = TRUE) +
# 
#     geom_point(data = as.data.frame(HDDS_IPC),aes(clust_HDDS, clust_HDDS_predict_ipc),shape =2,size =4,show.legend = FALSE,na.rm = TRUE) +
# 
#   annotate(geom = "text", size = 7, x = 4.7, y = 3.8, label = "III") +
#   annotate(geom = "text", size = 7, x = 6.5, y = 6.2, label = "III") +
#   annotate(geom = "text", size = 7, x = 4.7, y = 6.5, label = "I") +
#   annotate(geom = "text", size = 7, x = 4.7, y = 5.6, label = "II") +
#   annotate(geom = "text", size = 7, x = 6.5, y = 6.7, label = "II") +
#   annotate(geom = "text", size = 7, x = 6.5, y = 3.8, label = "IV") +
#   
#   theme(plot.margin = unit(c(1, 15, 1, 1), "lines")) 
# grid.text(paste("R Squared= ",r2list[3],sep = " "), x = unit(0.85, "npc"), y = unit(0.65, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("IPC only predictions in triangles", x = unit(0.85, "npc"), y = unit(0.62, "npc"),gp=gpar(fontsize=15)，just="left") 
# grid.text("Cluster model predictions in dots", x = unit(0.85, "npc"), y = unit(0.59, "npc"),gp=gpar(fontsize=15)，just="left")
# 
# 
# grid.text("HDDS of 6 or above is good diversity", x = unit(0.85, "npc"), y = unit(0.47, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("HDDS from 3 to 6 is medium diversity", x = unit(0.85, "npc"), y = unit(0.44, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("HDDS of value 3 or below is low diversity", x = unit(0.85, "npc"), y = unit(0.41, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area I:Overpredicting, actually medium", x = unit(0.85, "npc"), y = unit(0.38, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("diversity and predicted as good diversity", x = unit(0.85, "npc"), y = unit(0.35,"npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("Area II:Overpredicting,", x = unit(0.85, "npc"), y = unit(0.32, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("but within the same category", x = unit(0.85, "npc"), y = unit(0.29, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# 
# grid.text("Area III:Underpredicting,", x = unit(0.85, "npc"), y = unit(0.26, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("but within the same category", x = unit(0.85, "npc"), y = unit(0.23, "npc"),gp=gpar(fontsize=15),just="left") 
# 
# grid.text("Area IV:Underpredicting,actual medium", x = unit(0.85, "npc"), y = unit(0.2, "npc"),gp=gpar(fontsize=15),just="left") 
# grid.text("diversity and predicted as good diversity", x = unit(0.85, "npc"), y = unit(0.17, "npc"),gp=gpar(fontsize=15),just="left") 
# 



```

b.	Density plot (predication using different scales + household)
    i.	Unexplored variation of household level 
```{r,echo=FALSE}    
csv_list <- list.files(path="data/all_predict_2013", 
                    pattern = "csv$",
                    full.names=TRUE)
dfnames<-csv_list

# remove irregulars in the file names, 
pattern<-c("data/all_predict_2013/","clust_",".csv")
for (i in 1:length(pattern)) {
  dfnames <- gsub(pattern[i],"", dfnames)
}



list2env(
  lapply(setNames(csv_list, make.names(dfnames)), 
         function(i){read.csv(i)}), envir = .GlobalEnv)

predict_df<-cbind(logFCS_predict_m3[1],RCSI_predict_m3[1],HDDS_predict_m3[1])

for (i in 1:length(dfnames)){
  # exclude unneeded cols  
  temp <- get(dfnames[i])
  predict_df<-cbind(predict_df,temp[2])
}




malawi<- read.csv("data/cluster_fs.csv")
 
logFCS_IPC <- read.csv("data/all_ipc/logFCS_predict_CLUST_IPC.csv")
HDDS_IPC <- read.csv("data/all_ipc/HDDS_predict_CLUST_IPC.csv")
RCSI_IPC <- read.csv("data/all_ipc/RCSI_predict_CLUST_IPC.csv")

 
    
FCS_data<-cbind(predict_df$clust_logFCS_ipczone_predict_m3,predict_df$clust_logFCS_TA_predict_m3,predict_df$clust_logFCS_clust_predict_m3,predict_df$clust_logFCS,logFCS_IPC$clust_logFCS_predict_ipc)
colnames(FCS_data)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")
long_fcs<- melt(FCS_data,na.rm=TRUE)
colnames(long_fcs)<-c("no","level","logFCS")
plot_long<- long_fcs[long_fcs$level != "IPC_value_only",]
plot_long_ipc_fcs<- long_fcs[long_fcs$level == "IPC_value_only",]


plot_long_FCS= dplyr::bind_rows(plot_long, long_FCS_hh)



HDDS_data<-cbind(predict_df$clust_HDDS_ipczone_predict_m3,predict_df$clust_HDDS_TA_predict_m3,predict_df$clust_HDDS_clust_predict_m3,predict_df$clust_HDDS,HDDS_IPC$clust_HDDS_predict_ipc)
colnames(HDDS_data)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")
long_HDDS<- melt(HDDS_data,na.rm=TRUE)
colnames(long_HDDS)<-c("no","level","HDDS")
plot_long<- long_HDDS[long_HDDS$level != "IPC_value_only",]
plot_long_ipc_HDDS<- long_HDDS[long_HDDS$level == "IPC_value_only",]

plot_long_HDDS= dplyr::bind_rows(plot_long, long_HDDS_hh)


# rcsi P1 < 4
#P2 = 4-17
#P3 = 17-42
#P4/5 > 42
RCSI_data<-cbind(predict_df$clust_RCSI_ipczone_predict_m3,predict_df$clust_RCSI_TA_predict_m3,predict_df$clust_RCSI_clust_predict_m3,predict_df$clust_RCSI,RCSI_IPC$clust_RCSI_predict_ipc)
colnames(RCSI_data)<-c("IPC_zone","TA","cluster","Actual","IPC_value_only")
long_rcsi<- melt(RCSI_data,na.rm=TRUE)
colnames(long_rcsi)<-c("no","level","RCSI")
plot_long<- long_rcsi[long_rcsi$level != "IPC_value_only",]
plot_long_ipc_RCSI<- long_rcsi[long_rcsi$level == "IPC_value_only",]

plot_long_RCSI= dplyr::bind_rows(plot_long, long_RCSI_hh)


``` 

```{r,echo= FALSE}

#plot_long_FCS = plot_long_FCS %>% filter(level!="Actual" & level=="IPC_value_only")
# plot_long_HDDS = plot_long_HDDS %>% filter(level!="Household Actual" & level!="IPC_zone" & level!="TA" & level!="cluster")
# plot_long_FCS = plot_long_FCS %>% filter(level!="Household Actual" & level!="IPC_zone" & level!="TA" & level!="cluster")
# plot_long_RCSI = plot_long_RCSI %>% filter(level!="Household Actual" & level!="IPC_zone" & level!="TA" & level!="cluster")

#plot_long_RCSI = plot_long_RCSI %>% filter(level!="Household Actual")


p = ggplot(as.data.frame(plot_long_FCS),aes(x=logFCS,color=level)) + geom_density(alpha=0.1,lwd=1.5,show.legend = FALSE) +xlim(2.8, 4.9) +
geom_vline(xintercept=log(28),linetype=2) + geom_vline(xintercept=log(42),linetype=2)+
  stat_density(data=plot_long_ipc_fcs,aes(x=logFCS, y=..scaled..*3.5,color=level)) + scale_y_continuous(name= "Density",sec.axis = sec_axis(~.*28, name = " Density (IPC value only) ")) +  
 theme_classic()+
  theme(plot.title = element_text(size = 30, face = "bold"),
        # legend.title=element_text(size=30),
        # legend.text=element_text(size=30),
        axis.text.x=element_text(size=30),axis.text.y=element_text(size=30),
                 axis.title=element_text(size=30,face="bold") ) 

 p
 ggsave("output/figures/Density_new_FULL/fcs_ipc.png", width = 15, height = 15)

 
 
p= ggplot(as.data.frame(plot_long_HDDS),aes(x=HDDS, color=level))+ geom_density(alpha=0.20,lwd=1.5,show.legend = FALSE) +
  xlim(1.5, 7.6) + geom_vline(xintercept=3,linetype=2) + geom_vline(xintercept=6,linetype=2) +
  stat_density(data=plot_long_ipc_HDDS,aes(x=HDDS,y=..scaled..*1.1,color=level)) +
  scale_y_continuous(name= "Density",sec.axis = sec_axis(~.*12, name = "Density (IPC value only) "))  +  theme_classic()+
    theme(plot.title = element_text(size =30, face = "bold"),
          #legend.title=element_text(size=30), legend.text=element_text(size=30),
          axis.text.x=element_text(size=30),axis.text.y=element_text(size=30),
                 axis.title=element_text(size=30,face="bold") ) 

p
ggsave("output/figures/Density_new_FULL/hdds_ipc.png", width = 15, height = 15)
 
colnames(plot_long_RCSI)[3]="rCSI"
colnames(plot_long_ipc_RCSI)[3]="rCSI"



p = ggplot(as.data.frame(plot_long_RCSI),aes(x=rCSI, color=level))+ stat_density(data=plot_long_ipc_RCSI,aes(x=rCSI,y=..scaled../2.3,color=level)) + geom_density(alpha=0.30,lwd=1.5,show.legend = FALSE)+xlim(0, 45) + theme_classic()+
  geom_vline(xintercept=4,linetype=2) + geom_vline(xintercept=17,linetype=2)+ geom_vline(xintercept=42,linetype=2)+
   scale_y_continuous(name= "Density",sec.axis = sec_axis(~.*3.130, name = "Density (IPC value only) ")) +
    theme(plot.title = element_text(size = 30, face = "bold"),
#          legend.title=element_text(size=30), legend.text=element_text(size=30),
           axis.text.x=element_text(size=30),
axis.text.y=element_text(size=30),
                 axis.title=element_text(size=30,face="bold") ) 
p

ggsave("output/figures/Density_new_FULL/rcsi_ipc.png", width = 15, height = 15)

 
```
    
  
    
d.	 R Squared of 2013 predication 

```{r,echo=FALSE}
FCS_data_model3 =  FCS_data 
FCS_data_model3 = as.data.frame(FCS_data_model3) %>% dplyr::select(-IPC_value_only)

FCS_data_model0<-cbind(logFCS_IPC$clust_logFCS_predict_ipc,logFCS_IPC$clust_logFCS_predict_ipc,logFCS_IPC$clust_logFCS_predict_ipc,predict_df$clust_logFCS)
colnames(FCS_data_model0)<-c("IPC_zone","TA","cluster","Actual")


FCS_data_model2<-cbind(predict_df$clust_logFCS_ipczone_predict_m2,predict_df$clust_logFCS_TA_predict_m2,predict_df$clust_logFCS_clust_predict_m2,predict_df$clust_logFCS)
colnames(FCS_data_model2)<-c("IPC_zone","TA","cluster","Actual")


FCS_data_model1<-cbind(predict_df$clust_logFCS_ipczone_predict_m1,predict_df$clust_logFCS_TA_predict_m1,predict_df$clust_logFCS_clust_predict_m1,predict_df$clust_logFCS)
colnames(FCS_data_model1)<-c("IPC_zone","TA","cluster","Actual")

FCS_List<-list(FCS_data_model0,FCS_data_model1,FCS_data_model2,FCS_data_model3)

HDDS_data_model3 =  HDDS_data 
HDDS_data_model3 = as.data.frame(HDDS_data_model3) %>% dplyr::select(-IPC_value_only)


HDDS_data_model0<-cbind(HDDS_IPC$clust_HDDS_predict_ipc,HDDS_IPC$clust_HDDS_predict_ipc,HDDS_IPC$clust_HDDS_predict_ipc,predict_df$clust_HDDS)
colnames(HDDS_data_model0)<-c("IPC_zone","TA","cluster","Actual")

HDDS_data_model2<-cbind(predict_df$clust_HDDS_ipczone_predict_m2,predict_df$clust_HDDS_TA_predict_m2,predict_df$clust_HDDS_clust_predict_m2,predict_df$clust_HDDS)
colnames(HDDS_data_model2)<-c("IPC_zone","TA","cluster","Actual")



HDDS_data_model1<-cbind(predict_df$clust_HDDS_ipczone_predict_m1,predict_df$clust_HDDS_TA_predict_m1,predict_df$clust_HDDS_clust_predict_m1,predict_df$clust_HDDS)
colnames(HDDS_data_model1)<-c("IPC_zone","TA","cluster","Actual")

HDDS_List<-list(HDDS_data_model0,HDDS_data_model1,HDDS_data_model2,HDDS_data_model3)


RCSI_data_model3 =  RCSI_data 
RCSI_data_model3 = as.data.frame(RCSI_data_model3) %>% dplyr::select(-IPC_value_only)

RCSI_data_model0<-cbind(RCSI_IPC$clust_RCSI_predict_ipc,RCSI_IPC$clust_RCSI_predict_ipc,RCSI_IPC$clust_RCSI_predict_ipc,predict_df$clust_RCSI)
colnames(RCSI_data_model0)<-c("IPC_zone","TA","cluster","Actual")

 
RCSI_data_model2<-cbind(predict_df$clust_RCSI_ipczone_predict_m2,predict_df$clust_RCSI_TA_predict_m2,predict_df$clust_RCSI_clust_predict_m2,predict_df$clust_RCSI)
colnames(RCSI_data_model2)<-c("IPC_zone","TA","cluster","Actual")



RCSI_data_model1<-cbind(predict_df$clust_RCSI_ipczone_predict_m1,predict_df$clust_RCSI_TA_predict_m1,predict_df$clust_RCSI_clust_predict_m1,predict_df$clust_RCSI)
colnames(RCSI_data_model1)<-c("IPC_zone","TA","cluster","Actual")

RCSI_List<-list(RCSI_data_model0,RCSI_data_model1,RCSI_data_model2,RCSI_data_model3)
source("function/R2Compute.R")
source("function/R2ComputeDF.R")


r2mat_RCSI<- sapply(RCSI_List,R2ComputeDF)
r2mat_HDDS<- sapply(HDDS_List,R2ComputeDF)
r2mat_FCS<- sapply(FCS_List,R2ComputeDF)

colnames(r2mat_RCSI) = c("m0","m1","m2","m3")
colnames(r2mat_HDDS) = c("m0","m1","m2","m3")
colnames(r2mat_FCS) = c("m0","m1","m2","m3")

rownames(r2mat_RCSI) = c("IPC_zone","TA","cluster")
rownames(r2mat_HDDS) = c("IPC_zone","TA","cluster")
rownames(r2mat_FCS) = c("IPC_zone","TA","cluster")


r2matlist<-list(r2mat_FCS,r2mat_HDDS,r2mat_RCSI)

r2matlist<-lapply(r2matlist,as.data.frame)
r2matlist<-lapply(r2matlist,function(x){tibble::rownames_to_column(x,var = "Level")})

r2matlist<-lapply(r2matlist,function(x){tidyr::gather(data= x,key=model,2:5,value = rsquares)})

r2matlist[[1]]["measure"] ="logFCS"
r2matlist[[2]]["measure"] ="HDDS"
r2matlist[[3]]["measure"] ="rCSI"

r2 = bind_rows(r2matlist[[1]],r2matlist[[2]],r2matlist[[3]])
colnames(r2)[2] = "Model"
colnames(r2)[3] = "RSquared"
colnames(r2)[4] = "Measures"


r2$Level[r2$Level=="IPC_zone"]<-"IPC Zone"
r2$Level[r2$Level=="cluster"]<-"Cluster"



r2$Model[r2$Model=="m0"]<-"Class 0 (IPC value only)"
r2$Model[r2$Model=="m1"]<-"Class 1 data"
r2$Model[r2$Model=="m2"]<-"Class 1 + Class 2 data"
r2$Model[r2$Model=="m3"]<-"Class 1 + Class 2 + Class 3 data"


ord <- c("IPC_value_only","IPC Zone","TA","Cluster")
r2$Level <- factor(r2$Level,levels=ord)


ord_measure <- c("rCSI","logFCS","HDDS")
r2$Measures <- factor(r2$Measures,levels=ord_measure)


ord_m <- c("Class 0 (IPC value only)","Class 1 data","Class 1 + Class 2 data","Class 1 + Class 2 + Class 3 data")
r2$Model <- factor(r2$Model,levels=ord_m)

r2$RSquared <-as.numeric(r2$RSquared)



``` 
    
```{r,echo=FALSE}

#r20 = r2 %>% filter(Model == "Class 0 (IPC value only)" |Model == "Class 1 data" |Model == "Class 1 + Class 2 data"  )

rplot<-ggplot(data = r2, aes(x =Level, y = RSquared,colour = Measures ,shape = Model)) 
rplot<-rplot + geom_point(size=7) + scale_y_continuous(limits = c(0, 0.63))
rplot<-rplot + labs( x = "Geo-spatial Level", y = "R Squared")

rplot <- rplot+ theme_classic()  
rplot <- rplot +  theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
                 axis.title=element_text(size=17,face="bold") ) 

 #rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)
 
 # +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
 rplot
#  grid.text("Class 1 data contains: past IPC values, precipitation,", x = unit(0.630, "npc"), y = unit(0.35, "npc"),gp=gpar(fontsize=15), check.overlap = TRUE,just="left") 
#  grid.text("market prices, market access measures, and soil quality", x = unit(0.630, "npc"), y = unit(0.32, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left") 
# grid.text("Class 2 data contains: share of households owing cellular", x = unit(0.630, "npc"), y = unit(0.29, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")
# grid.text("phone and share of dwellings with metal versus thatch roof", x = unit(0.630, "npc"), y = unit(0.26, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")
# grid.text("Class 3 data contains: household demographics and assets", x = unit(0.630, "npc"), y = unit(0.23, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")


```

```{r,echo=FALSE}

r22 = bind_rows(r2matlist[[1]],r2matlist[[2]],r2matlist[[3]])
colnames(r22)[2] = "Model"
colnames(r22)[3] = "RSquared"
colnames(r22)[4] = "Measures"


r22$Level[r22$Level=="IPC_zone"]<-"IPC Zone"
r22$Level[r22$Level=="cluster"]<-"Cluster"
r22$Model[r22$Model=="m0"]<-"Class 0: IPC value only"
r22$Model[r22$Model=="m1"]<-"Class 1"
r22$Model[r22$Model=="m2"]<-"Class 1 + Class 2  "
r22$Model[r22$Model=="m3"]<-"Class 1 + Class 2 + Class 3"

ord <- c("IPC_value_only","IPC Zone","TA","Cluster")
r22$Level <- factor(r22$Level,levels=ord)

r22$RSquared <-as.numeric(r22$RSquared)

r22 = r22 %>% arrange(Model)

rplot<-ggplot(data = r22, aes(x =Model , y = RSquared,colour =Level  ,shape = Measures)) 
rplot<-rplot + geom_point(size=7)
rplot<-rplot + labs( x = "Model", y = "R Squared")

rplot <- rplot+ theme_classic() 
rplot <- rplot +  theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=18),axis.text.x=element_text(size=15),axis.text.y=element_text(size=15),
                 axis.title=element_text(size=17,face="bold") ) 

 rplot = rplot + scale_color_grey(start = 0.8, end = 0.2) +  theme(plot.margin = unit(c(1, 9, 1, 1), "lines"))  
 rplot
 grid.text("Class 1 data contains:", x = unit(0.77, "npc"), y = unit(0.35, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left") 
  grid.text("past IPC values, precipitation,", x = unit(0.77, "npc"), y = unit(0.32, "npc"),gp=gpar(fontsize=15), check.overlap = TRUE,just="left") 
 grid.text("market prices, market access", x = unit(0.77, "npc"), y = unit(0.29, "npc"),gp=gpar(fontsize=15), check.overlap = TRUE,just="left") 
 grid.text("measures, and soil quality.", x = unit(0.77, "npc"), y = unit(0.26, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left") 
grid.text("Class 2 data contains: ", x = unit(0.77, "npc"), y = unit(0.23, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")
grid.text("share of households owing cellular", x = unit(0.77, "npc"), y = unit(0.20, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")
grid.text("phone and share of dwellings", x = unit(0.77, "npc"), y = unit(0.17, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")
grid.text("with metal versus thatch roof.", x = unit(0.77, "npc"), y = unit(0.14, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")

grid.text("Class 3 data contains:", x = unit(0.77, "npc"), y = unit(0.11, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")
grid.text("household demographics and assets.", x = unit(0.77, "npc"), y = unit(0.08, "npc"),gp=gpar(fontsize=15),check.overlap = TRUE,just="left")

```
    
f.	 Discussion of classification 
g.  hit and miss tables (for the predications) 
    i.	one is cluster to actual cluster outcomes 
    
    
```{r,echo=FALSE}
library(caret)
logFCS <- read.csv("data/all_predict/clust_logFCS_predict_clust_m3.csv")
HDDS <- read.csv("data/all_predict/clust_HDDS_predict_clust_m3.csv")
RCSI <- read.csv("data/all_predict/clust_RCSI_predict_clust_m3.csv")

colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")

#"Poor_predict","Borderline_predict","Acceptable_predict"
# Poor_actual","Borderline_actual","Acceptable_actual"

# calculate the percentage of that samples that are underpredicting. 
diff_fcs =logFCS$logFCS_predict  - logFCS$logFCS 
diff_fcs_dum = ifelse(diff_fcs>0,1,0)
mean(diff_fcs_dum)
1- mean(diff_fcs_dum)



diff_HDDS =HDDS$HDDS_predict  - HDDS$HDDS
diff_HDDS_dum = ifelse(diff_HDDS>0,1,0)
mean(diff_HDDS_dum)
1- mean(diff_HDDS_dum)



diff_rcsi =RCSI$RCSI_predict  - RCSI$RCSI
diff_rcsi_dum = ifelse(diff_rcsi>0,1,0)
mean(diff_rcsi_dum)
1- mean(diff_rcsi_dum)




logFCS$cat_logFCS<-cut(logFCS$logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS$cat_logFCS_predict<-cut(logFCS$logFCS_predict, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
print("logFCS confusionMatrix")

confusionMatrix(logFCS$cat_logFCS_predict,logFCS$cat_logFCS)

# HDDS 3 6 
HDDS$cat_HDDS<-cut(HDDS$HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS$cat_HDDS_predict<-cut(HDDS$HDDS_predict, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
print("HDDS confusionMatrix")
confusionMatrix(HDDS$cat_HDDS_predict,HDDS$cat_HDDS)



RCSI$cat_RCSI<-cut(RCSI$RCSI, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
RCSI$cat_RCSI_predict<-cut(RCSI$RCSI_predict, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))

print("RCSI confusionMatrix")

confusionMatrix(RCSI$cat_RCSI_predict,RCSI$cat_RCSI)


```
    
```{r}
    library(caret)
logFCS <- read.csv("data/all_predict/clust_logFCS_predict_ipczone_m3.csv")
HDDS <- read.csv("data/all_predict/clust_HDDS_predict_ipczone_m3.csv")
RCSI <- read.csv("data/all_predict/clust_RCSI_predict_ipczone_m3.csv")

colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")

#"Poor_predict","Borderline_predict","Acceptable_predict"
# Poor_actual","Borderline_actual","Acceptable_actual"

# calculate the percentage of that samples that are underpredicting. 
diff_fcs =logFCS$logFCS_predict  - logFCS$logFCS 
diff_fcs_dum = ifelse(diff_fcs>0,1,0)
mean(diff_fcs_dum)
1- mean(diff_fcs_dum)



diff_HDDS =HDDS$HDDS_predict  - HDDS$HDDS
diff_HDDS_dum = ifelse(diff_HDDS>0,1,0)
mean(diff_HDDS_dum)
1- mean(diff_HDDS_dum)



diff_rcsi =RCSI$RCSI_predict  - RCSI$RCSI
diff_rcsi_dum = ifelse(diff_rcsi>0,1,0)
mean(diff_rcsi_dum)
1- mean(diff_rcsi_dum)




logFCS$cat_logFCS<-cut(logFCS$logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS$cat_logFCS_predict<-cut(logFCS$logFCS_predict, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
print("logFCS confusionMatrix")

confusionMatrix(logFCS$cat_logFCS_predict,logFCS$cat_logFCS)

# HDDS 3 6 
HDDS$cat_HDDS<-cut(HDDS$HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS$cat_HDDS_predict<-cut(HDDS$HDDS_predict, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
print("HDDS confusionMatrix")
confusionMatrix(HDDS$cat_HDDS_predict,HDDS$cat_HDDS)



RCSI$cat_RCSI<-cut(RCSI$RCSI, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
RCSI$cat_RCSI_predict<-cut(RCSI$RCSI_predict, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))

print("RCSI confusionMatrix")

confusionMatrix(RCSI$cat_RCSI_predict,RCSI$cat_RCSI)


```
    
    
    
    
    
    
```{r,include=FALSE}
hh_2010 <- read.csv("data/IHS2010.csv")
hh_2013 = read.csv("data/IHS2013.csv")


rcsi_formula_hh<-formula_compose("RCSI",clust_vars)
logFCS_formula_hh<-formula_compose("logFCS",clust_vars)
HDDS_formula_hh<-formula_compose("HDDS",clust_vars)

rcsi_coord <- cbind(clust_2013$clust, rcsi_predictions)
logFCS_coord <- cbind(clust_2013$clust, logFCS_predictions)
HDDS_coord <- cbind(clust_2013$clust, HDDS_predictions)

colnames(rcsi_coord) = c("clust","rcsi_predict")
colnames(logFCS_coord) = c("clust","logFCS_predict")
colnames(HDDS_coord) = c("clust","HDDS_predict")


rcsi_predictions_hh<-linear_fit(rcsi_formula_hh,hh_2010,hh_2013)
logFCS_predictions_hh<-linear_fit(logFCS_formula_hh,hh_2010,hh_2013) 
HDDS_predictions_hh<-linear_fit(HDDS_formula_hh,hh_2010,hh_2013) 

```
    
    
   ii.	cluster predication to actual household level outcomes 
```{r,echo=FALSE}

hh_actual  = hh_2010 %>% select(clust,logFCS,HDDS,RCSI) %>% na.omit()


hh_join = dplyr::left_join(hh_actual,as.data.frame(rcsi_coord) , by = "clust")
hh_join = dplyr::left_join(hh_join,as.data.frame(logFCS_coord) , by = "clust")
hh_join = dplyr::left_join(hh_join,as.data.frame(HDDS_coord) , by = "clust")


logFCS = hh_join %>% select(logFCS,logFCS_predict)
RCSI = hh_join %>% select(RCSI,rcsi_predict)
HDDS = hh_join %>% select(HDDS,HDDS_predict)


colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")

#"Poor_predict","Borderline_predict","Acceptable_predict"
# Poor_actual","Borderline_actual","Acceptable_actual"

logFCS$cat_logFCS<-cut(logFCS$logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS$cat_logFCS_predict<-cut(logFCS$logFCS_predict, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))

print("logFCS confusionMatrix")

confusionMatrix(logFCS$cat_logFCS_predict,logFCS$cat_logFCS)


# HDDS 3 6 
HDDS$cat_HDDS<-cut(HDDS$HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS$cat_HDDS_predict<-cut(HDDS$HDDS_predict, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))

print("HDDS confusionMatrix")
confusionMatrix(HDDS$cat_HDDS_predict,HDDS$cat_HDDS)



RCSI$cat_RCSI<-cut(RCSI$RCSI, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
RCSI$cat_RCSI_predict<-cut(RCSI$RCSI_predict, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))

print("RCSI confusionMatrix")
confusionMatrix(RCSI$cat_RCSI_predict,RCSI$cat_RCSI)

```



try the Tail only predictions 

```{r,echo=FALSE}

################################################ 
# generatea the categorized actual 
#####################################################
logFCS <- read.csv("data/all_predict/logFCS/clust_logFCS_predict_clust_m3.csv")
HDDS <- read.csv("data/all_predict/HDDS/clust_HDDS_predict_clust_m3.csv")
RCSI <- read.csv("data/all_predict/RCSI/clust_RCSI_predict_clust_m3.csv")

colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")

actual_logFCS = logFCS$logFCS
actual_HDDS = HDDS$HDDS
actual_RCSI = RCSI$RCSI

cat_logFCS<-cut(actual_logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
cat_HDDS<-cut(actual_HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
cat_RCSI<-cut(actual_RCSI, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))


#"Poor_predict","Borderline_predict","Acceptable_predict"
# Poor_actual","Borderline_actual","Acceptable_actual"


logFCS_full_list= list.files("data/all_predict/logFCS",full.names = TRUE)
HDDS_full_list= list.files("data/all_predict/HDDS",full.names = TRUE)
RCSI_full_list= list.files("data/all_predict/RCSI",full.names = TRUE)


model_name = gsub("data/all_predict/logFCS/clust_","",logFCS_full_list)
model_name = gsub(".csv","",model_name)
model_name = gsub("_predict","",model_name)


info_master = data.frame(model=model_name[1],accuracy=0,type1=0,type2=0)
info_master
  
for (i in 1:length(logFCS_full_list)){
  temp_file  = read.csv(logFCS_full_list[i])
  cat_logFCS_pred<-cut(temp_file[,2], c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
  confu_mat= as.matrix(confusionMatrix(cat_logFCS_pred,cat_logFCS))
  accuracy = sum(diag(confu_mat))/sum(rowSums(confu_mat))
  # lower =  predict to be better than actual, over prediction 
  type2 = sum(confu_mat[lower.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  type1 = sum(confu_mat[upper.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  model = model_name[i]
  info_table = data.frame(model,accuracy,type1,type2)
  info_master = bind_rows(info_master,info_table)
  }

info_master



model_name = gsub("data/all_predict/HDDS/clust_","",HDDS_full_list)
model_name = gsub(".csv","",model_name)
model_name = gsub("_predict","",model_name)

for (i in 1:length(HDDS_full_list)){
  temp_file  = read.csv(HDDS_full_list[i])
  cat_HDDS_pred<-cut(temp_file[,2], c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
  confu_mat= as.matrix(confusionMatrix(cat_HDDS_pred,cat_HDDS))
  accuracy = sum(diag(confu_mat))/sum(rowSums(confu_mat))
  # lower =  predict to be better than actual, over prediction 
  type2 = sum(confu_mat[lower.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  type1 = sum(confu_mat[upper.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  model = model_name[i]
  info_table = data.frame(model,accuracy,type1,type2)
  info_master = bind_rows(info_master,info_table)
  }

info_master

model_name = gsub("data/all_predict/RCSI/clust_","",RCSI_full_list)
model_name = gsub(".csv","",model_name)
model_name = gsub("_predict","",model_name)

for (i in 1:length(RCSI_full_list)){
  temp_file  = read.csv(RCSI_full_list[i])
  cat_RCSI_pred<-cut(temp_file[,2], c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
  confu_mat= as.matrix(confusionMatrix(cat_RCSI_pred,cat_RCSI))
  accuracy = sum(diag(confu_mat))/sum(rowSums(confu_mat))
  # lower =  predict to be better than actual, over prediction 
  type2 = sum(confu_mat[upper.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  type1 = sum(confu_mat[lower.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  model = model_name[i]
  info_table = data.frame(model,accuracy,type1,type2)
  info_master = bind_rows(info_master,info_table)
}
confu_mat

info_master
```


Maybe we can collapse them into a couple of tables by having the following columns: % correct, % type I, % type II and a different row for each model.

```{r,include=FALSE}
logFCS_tail_list= list.files("data/all_tail_predictions/logFCS",full.names = TRUE)
HDDS_tail_list= list.files("data/all_tail_predictions/HDDS",full.names = TRUE)
RCSI_tail_list= list.files("data/all_tail_predictions/RCSI",full.names = TRUE)
model_name = gsub("data/all_tail_predictions/logFCS/","",logFCS_tail_list)
model_name = gsub(".csv","",model_name)
model_name = gsub("_predict","",model_name)
logFCS_tail_list

info_tail = data.frame(model=model_name[1],accuracy=0,type1=0,type2=0)
info_tail

for (i in 1:length(logFCS_tail_list)){
  temp_file  = read.csv(logFCS_tail_list[i])
  cat_logFCS_pred<-cut(temp_file[,1], c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
  confu_mat= as.matrix(confusionMatrix(cat_logFCS_pred,cat_logFCS))
  accuracy = sum(diag(confu_mat))/sum(rowSums(confu_mat))
  # lower =  predict to be better than actual, over prediction 
  type2 = sum(confu_mat[lower.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  type1 = sum(confu_mat[upper.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  model = model_name[i]
  info_table = data.frame(model,accuracy,type1,type2)
  info_tail = bind_rows(info_tail,info_table)
}

info_tail

model_name = gsub("data/all_tail_predictions/HDDS/","",HDDS_tail_list)
model_name = gsub(".csv","",model_name)
model_name = gsub("_predict","",model_name)

for (i in 1:length(HDDS_tail_list)){
  temp_file  = read.csv(HDDS_tail_list[i])
  cat_HDDS_pred<-cut(temp_file[,1], c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
  confu_mat= as.matrix(confusionMatrix(cat_HDDS_pred,cat_HDDS))
  accuracy = sum(diag(confu_mat))/sum(rowSums(confu_mat))
  # lower =  predict to be better than actual, over prediction 
  type2 = sum(confu_mat[lower.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  type1 = sum(confu_mat[upper.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  model = model_name[i]
  info_table = data.frame(model,accuracy,type1,type2)
  info_tail = bind_rows(info_tail,info_table)
}


model_name = gsub("data/all_tail_predictions/RCSI/","",RCSI_tail_list)
model_name = gsub(".csv","",model_name)
model_name = gsub("_predict","",model_name)

for (i in 1:length(RCSI_tail_list)){
  temp_file  = read.csv(RCSI_tail_list[i])
  cat_RCSI_pred<-cut(temp_file[,1], c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
  confu_mat= as.matrix(confusionMatrix(cat_RCSI_pred,cat_RCSI))
  accuracy = sum(diag(confu_mat))/sum(rowSums(confu_mat))
  # lower =  predict to be better than actual, over prediction 
  type2 = sum(confu_mat[upper.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  type1 = sum(confu_mat[lower.tri(confu_mat, diag = FALSE)])/sum(rowSums(confu_mat))
  model = model_name[i]
  info_table = data.frame(model,accuracy,type1,type2)
  info_tail = bind_rows(info_tail,info_table)
}


info_tail

write.csv(info_tail,"output/info_tail.csv")
write.csv(info_master,"output/info_master.csv")
```


```{r,include=False}

tail = read.csv("output/info_tail_full.csv")
full = read.csv("output/info_master_full.csv")
# 
tail$Model = as.character(tail$Model)
tail$Model[tail$Model=="m1"]<-"Class 1 data"
tail$Model[tail$Model=="m2"]<-"Class 1 + Class 2 data"
tail$Model[tail$Model=="m3"]<-"Class 1 + Class 2 + Class 3 data"

full$Model = as.character(full$Model)

full$Model[full$Model=="m1"]<-"Class 1 data"
full$Model[full$Model=="m2"]<-"Class 1 + Class 2 data"
full$Model[full$Model=="m3"]<-"Class 1 + Class 2 + Class 3 data"
# 

ord <- c("IPC Zone","TA","Cluster")
full$Level <- factor(full$Level,levels=ord)

ord_measure <- c("rCSI","logFCS","HDDS")
full$FS.Measure <- factor(full$FS.Measure,levels=ord_measure)

# 
ord_m <- c("Class 1 data","Class 1 + Class 2 data","Class 1 + Class 2 + Class 3 data")
full$Model <- factor(full$Model,levels=ord_m)


ord <- c("IPC Zone","TA","Cluster")
tail$Level <- factor(tail$Level,levels=ord)

ord_measure <- c("rCSI","logFCS","HDDS")
tail$FS.Measure <- factor(tail$FS.Measure,levels=ord_measure)



ord_measure <- c("rCSI","logFCS","HDDS")
tail$FS.Measure <- factor(tail$FS.Measure,levels=ord_measure)


ord_s <- c("Accuracy","% Type I","% Type II")
tail$Model.Measure <- factor(tail$Model.Measure,levels=ord_s)
full$Model.Measure <- factor(full$Model.Measure,levels=ord_s)



ord_m <- c("Class 1 data","Class 1 + Class 2 data","Class 1 + Class 2 + Class 3 data")
tail$Model <- factor(tail$Model,levels=ord_m)
 

# 
# colnames(full)[5] = "Type I Error"
# colnames(full)[6] = "Type II Error"
# 
# 
# colnames(tail)[5] = "Type I Error"
# colnames(tail)[6] = "Type II Error"

```

```{r,echo=FALSE}

FCS_full = full %>% filter(FS.Measure == "logFCS")

rplot<-ggplot(data = FCS_full, aes(x =Level, y = Value,shape=Model)) 
rplot<-rplot + geom_point(size=7,color='#00BA38',show.legend=FALSE)   +  facet_grid(. ~  Model.Measure)        

rplot<-rplot + labs( x = "Geo-spatial Level", y = "Accuracy/Type I/Type II")

rplot <- rplot    + theme_classic() theme(strip.text.x = element_text(size = 25))

rplot <- rplot +  theme(plot.title = element_text(size = 25, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=25),axis.text.x=element_text(size=25),axis.text.y=element_text(size=25),
                 axis.title=element_text(size=35,face="bold") ) 

 #rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)
 
 # +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
 rplot

ggsave("output/figures/accuracy/fcs_full.png", width = 15, height = 15)


``` 

```{r,echo=FALSE}

HDDS = full %>% filter(FS.Measure == "HDDS")

rplot<-ggplot(data = HDDS, aes(x =Level, y = Value,shape=Model))  
rplot<-rplot + geom_point(size=7,color='#619CFF',show.legend = FALSE)   +  facet_grid(. ~  Model.Measure) 
rplot<-rplot + labs( x = "Geo-spatial Level", y = "Accuracy/Type I/Type II")  

rplot <- rplot    + theme_classic() + theme(strip.text.x = element_text(size = 25))

rplot <- rplot +  theme(plot.title = element_text(size = 25, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=25),axis.text.x=element_text(size=25),axis.text.y=element_text(size=25),
                 axis.title=element_text(size=35,face="bold") ) 
 

 #rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)
 
 # +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
 rplot

ggsave("output/figures/accuracy/hdds_full.png", width = 15, height = 15)


``` 

```{r,echo=FALSE}

rCSI = full %>% filter(FS.Measure == "rCSI")

rplot<-ggplot(data = rCSI, aes(x =Level, y = Value,shape=Model)) 
rplot<-rplot +  geom_point(size=7,color='#F8766D',show.legend = FALSE)   +  facet_grid(. ~  Model.Measure) 
rplot<-rplot + labs( x = "Geo-spatial Level", y = "Accuracy/Type I/Type II")

rplot <- rplot    + theme_classic() + theme(strip.text.x = element_text(size = 25))

rplot <- rplot +  theme(plot.title = element_text(size = 25, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=25),axis.text.x=element_text(size=25),axis.text.y=element_text(size=25),
                 axis.title=element_text(size=35,face="bold") ) 
 

 #rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)
 
 # +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
 rplot

ggsave("output/figures/accuracy/rCSI_full.png", width = 15, height = 15)


``` 

```{r,echo=FALSE}

FCS_tail = tail %>% filter(FS.Measure == "logFCS")

rplot<-ggplot(data = FCS_tail, aes(x =Level, y = Value,shape=Model)) 
rplot<-rplot + geom_point(size=7,color='#00BA38',show.legend = FALSE)   +  facet_grid(. ~  Model.Measure)
rplot<-rplot + labs( x = "Geo-spatial Level", y = "Accuracy/Type I/Type II")


rplot <- rplot    + theme_classic() + theme(strip.text.x = element_text(size = 25))

rplot <- rplot +  theme(plot.title = element_text(size = 25, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=25),axis.text.x=element_text(size=25),axis.text.y=element_text(size=25),
                 axis.title=element_text(size=35,face="bold") ) 
 

#rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)

# +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
rplot

ggsave("output/figures/accuracy/fcs_tail.png", width = 15, height = 15)


``` 

```{r,echo=FALSE}

HDDS = tail %>% filter(FS.Measure == "HDDS")

rplot<-ggplot(data = HDDS, aes(x =Level, y = Value,shape=Model)) 
rplot<-rplot + geom_point(size=7,color='#619CFF',show.legend = FALSE)   +  facet_grid(. ~  Model.Measure) 
rplot<-rplot + labs( x = "Geo-spatial Level", y = "Accuracy/Type I/Type II")

rplot <- rplot    + theme_classic() + theme(strip.text.x = element_text(size = 25))

rplot <- rplot +  theme(plot.title = element_text(size = 25, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=25),axis.text.x=element_text(size=25),axis.text.y=element_text(size=25),
                 axis.title=element_text(size=35,face="bold") ) 
 
#rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)

# +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
rplot

ggsave("output/figures/accuracy/hdds_tail.png", width = 15, height = 15)


``` 

```{r,echo=FALSE}

rCSI = tail %>% filter(FS.Measure == "rCSI")
 
rplot<-ggplot(data = rCSI, aes(x =Level, y = Value,shape=Model)) 
rplot<-rplot +  geom_point(size=7,color='#F8766D',show.legend = FALSE)   +  facet_grid(. ~  Model.Measure) 
rplot<-rplot + labs( x = "Geo-spatial Level", y = "Accuracy/Type I/Type II")

rplot <- rplot    + theme_classic() + theme(strip.text.x = element_text(size = 25))

rplot <- rplot +  theme(plot.title = element_text(size = 25, face = "bold"),legend.title=element_text(size=20), legend.text=element_text(size=25),axis.text.x=element_text(size=25),axis.text.y=element_text(size=25),
                 axis.title=element_text(size=35,face="bold") ) 
 
#rplot = rplot + scale_color_grey(start = 0.8, end = 0.2)

# +  theme(plot.margin = unit(c(1, 2, 1, 1), "lines"))  
rplot

ggsave("output/figures/accuracy/rCSI_tail.png", width = 15, height = 15)


``` 
    1.	how bad it can be to just target the cluster level ?
    
    
    2.	put it in SI ? 
    
    
    
3.	2010 data (only what matters for 2010 is the tables (coefficients and variables))

a.	regression results 




b.	discussion on the coefficients 






```{r,include=FALSE}
# train= clust_2010 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              clust_logFCS,clust_RCSI,clust_HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# test= clust_2013 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              clust_logFCS,clust_RCSI,clust_HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# write.csv(train,"train.csv")
# write.csv(test,"test.csv")

```

```{r,include=FALSE}
# library(dplyr)
# trainHH= IHS2010 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              logFCS,RCSI,HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# testHH= IHS2013 %>% dplyr::select(clust_L12raincytot,clust_L12day1rain,clust_L12maxdays,clust_floodmax,clust_cells_own,
#                             clust_price,clust_thinn,clust_roof,clust_hhsize,clust_hh_age,clust_hh_gender,clust_asset,
#                              clust_dist_road,clust_dist_admarc,clust_percent_ag,clust_nutri_reten_constrained,clust_elevation,
#                              logFCS,RCSI,HDDS, ipc_lag1,ipc_lag12
#                              )
# 
# write.csv(trainHH,"trainhh.csv")
# write.csv(testHH,"testhh.csv")

```

```{r,include= FALSE}
cat("the overlapping months in 2010 and 2013 are" ,as.character(unique(clust_2013$month)))

common_lhz= intersect(unique(clust_2010$fnid),unique(clust_2013$fnid))

cat("and the number of overlapping ipc zones is" ,length(common_lhz))
```



```{r,include= FALSE}
library("ggpubr")
ggscatter(logFCS_pair, x = "actual", y = "predict",
          add = "reg.line", conf.int = TRUE,
          cor.coef = FALSE, cor.method = "pearson",
          xlab = "actual", ylab = "predict")

ggsave("logFCS_scatter.png", plot = last_plot(),device = "png",path = "output/figures/",
       dpi = 1000, limitsize = TRUE)

ggscatter(d, x ="RCSI_cluster" , y = "RCSI_pred",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "actual", ylab = "predict")

ggsave("RCSI_scatter.png", plot = last_plot(),device = "png",path = "output/figures/",
       dpi = 1000, limitsize = TRUE)

ggscatter(d, x ="HDDS_cluster" , y = "HDDS_pred",
          add = "reg.line", conf.int = TRUE,
          cor.coef = FALSE, cor.method = "pearson",
          xlab = "actual", ylab = "predict")

ggsave("HDDS_scatter.png", plot = last_plot(),device = "png",path = "output/figures/",
       dpi = 1000, limitsize = TRUE)


```



 ipc only value 
```{r,include=FALSE}
logFCS_IPC <- read.csv("data/all_ipc/logFCS_predict_CLUST_IPC.csv")
HDDS_IPC <- read.csv("data/all_ipc/HDDS_predict_CLUST_IPC.csv")
RCSI_IPC <- read.csv("data/all_ipc/RCSI_predict_CLUST_IPC.csv")

table(logFCS_IPC$clust_logFCS)

ggscatter(logFCS_IPC, x = "clust_logFCS", y = "clust_logFCS_predict_ipc",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "actual", ylab = "predict")
# 
library("ggpubr")
cor.test(HDDS_IPC$clust_HDDS, HDDS_IPC$clust_HDDS_predict_ipc, method="pearson")
cor.test(logFCS_IPC$clust_logFCS, logFCS_IPC$clust_logFCS_predict_ipc, method="pearson")
cor.test(RCSI_IPC$clust_RCSI, RCSI_IPC$clust_RCSI_predict_ipc, method="pearson")

cor.test(HDDS_IPC$clust_HDDS, HDDS_IPC$clust_HDDS_predict_ipc, method="pearson")
logFCS_pair = as.data.frame(logFCS_pair)
cor.test(logFCS_pair$predict, logFCS_pair$actual, method="pearson")
cor.test(RCSI_IPC$clust_RCSI, RCSI_IPC$clust_RCSI_predict_ipc, method="pearson")



library(caret)
# HDDS 3 6 
HDDS_IPC$cat_HDDS<-cut(HDDS_IPC$clust_HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS_IPC$cat_HDDS_predict<-cut(HDDS_IPC$clust_HDDS_predict_ipc, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
print("HDDS confusionMatrix")
confusionMatrix(HDDS_IPC$cat_HDDS_predict,HDDS_IPC$cat_HDDS)



logFCS_IPC$cat_logFCS<-cut(logFCS_IPC$clust_logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS_IPC$cat_logFCS_predict<-cut(logFCS_IPC$clust_logFCS_predict_ipc, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
print("logFCS confusionMatrix")

confusionMatrix(logFCS_IPC$cat_logFCS_predict,logFCS_IPC$cat_logFCS)





RCSI_IPC$cat_RCSI<-cut(RCSI_IPC$clust_RCSI, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
RCSI_IPC$cat_RCSI_predict<-cut(RCSI_IPC$clust_RCSI_predict_ipc, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))

print("RCSI confusionMatrix")

confusionMatrix(RCSI_IPC$cat_RCSI_predict,RCSI_IPC$cat_RCSI)


```

```{R}
   library(caret)
logFCS <- read.csv("data/all_predict/logFCS/clust_logFCS_predict_ipczone_m3.csv")
HDDS <- read.csv("data/all_predict/HDDS/clust_HDDS_predict_ipczone_m3.csv")
RCSI <- read.csv("data/all_predict/RCSI/clust_RCSI_predict_ipczone_m3.csv")

colnames(logFCS)<-c("logFCS","logFCS_predict")
colnames(HDDS)<-c("HDDS","HDDS_predict")
colnames(RCSI)<-c("RCSI","RCSI_predict")
 



logFCS$cat_logFCS<-cut(logFCS$logFCS, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
logFCS$cat_logFCS_predict<-cut(logFCS$logFCS_predict, c(0,log(28), log(42),Inf),labels=c("Poor","Borderline","Acceptable"))
print("logFCS confusionMatrix")

confusionMatrix(logFCS$cat_logFCS_predict,logFCS$cat_logFCS)

# HDDS 3 6 
HDDS$cat_HDDS<-cut(HDDS$HDDS, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
HDDS$cat_HDDS_predict<-cut(HDDS$HDDS_predict, c(0,3, 6,Inf),labels=c("Low Diversity","Medium Diversity","Good Diversity"))
print("HDDS confusionMatrix")
confusionMatrix(HDDS$cat_HDDS_predict,HDDS$cat_HDDS)



RCSI$cat_RCSI<-cut(RCSI$RCSI, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))
RCSI$cat_RCSI_predict<-cut(RCSI$RCSI_predict, c(-Inf,4,17,42,Inf),labels=c("Food Secure","Mild","Moderate","Severe"))

print("RCSI confusionMatrix")

confusionMatrix(RCSI$cat_RCSI_predict,RCSI$cat_RCSI)

